### 2019-11-18 docs/article.tex
Só uma organizada

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
% \usepackage{cite}
% Enables Portuguese Brasil
% \usepackage[portuguese]{babel}
%encoding
% Enables code listing
\usepackage{listings}
%--------------------------------------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
%--------------------------------------
%Enables the use of greek letter without a math context
\usepackage{textgreek}
%--------------------------------------
%Enables hiperlinks
\usepackage[hidelinks]{hyperref}
%--------------------------------------

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}

% The code style
\usepackage{color}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
	backgroundcolor=\color{backcolour},   
	commentstyle=\color{codegreen},
	keywordstyle=\color{magenta},
	numberstyle=\tiny\color{codegray},
	stringstyle=\color{codepurple},
	basicstyle=\footnotesize,
	breakatwhitespace=false,         
	breaklines=true,                 
	captionpos=b,                    
	keepspaces=true,                 
	numbers=left,                    
	numbersep=2pt,                  
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=2
}
\lstset{style=mystyle}
%---------------------------------------

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Classification of Histopathological Images of Breast Cells between Malignant and Benign Tumors based on Handcrafted Feature Extraction}
\author{André Furlan \& Hiago Matheus Brajato - UNESP - Universidade Estadual Paulista "Júlio de Mesquita Filho"}
\date{2019-11-14}
\maketitle

\begin{abstract}
According to the recent survey published by the International Agency for Research on Cancer (IARC), the breast cancer is one of the most common kinds of cancers diagnosed in the population nowadays. The diagnosis of this type of disease is usually made through the analysis of the breast cells by a specialist after the biopsy and staining, normally made by the combination of hematoxylin and eosin (H \& E). This manual assessment is a time-consuming task and depends on the expertise and perception of the pathologists. In order to overcome this limitations, image processing can be considered as great aid alternative. In this paper is presented an application for the classification of breast cell images between malignant and benign tumors. The developed software includes the principals steps present within the image processing field, such as preprocessing, segmentation, feature extraction and classification, in order to achieve good results in the analysis of a dataset composed by 50 images of malignant and benign tumors.
\end{abstract}

\begin{IEEEkeywords}
Breast Cancer, Image Processing, Diagnosis, Malignant and Benign
\end{IEEEkeywords}

\section{Introduction}
Breast Cancer is a kind of malignant tumor in which cells in the breast grow out of control. In a recent survey called GLOBOCAN \cite{GLOBOCAN} published in 2018 by the IARC, can be visualized the statistics about this type of cancer around the world. The study states that the breast cancer is the second most incident type of cancer in world, with 2 088 049 cases of this disease in the last year, and the number of cases of mortality is equals to 626 679 (about 30\% of total). According to the same study, the breast cancer is the most incident type in Brazil, with 85 620 registered cases in total, and the second most reason of mortalities among the cancers, with 18 842 cases, what represents 22\% of the total cases of breast cancer in Brazil. Figures 1 and 2 in the right graph the information presented until now. In the first chart is possible to visualize the statistics about the world, and in the second one is presented the numbers of cases in Brazil.

\begin{figure}[h]
    \centering
    \includegraphics[width=8cm]{Figuras/graphic1.png}
    \caption{Statistics about Incidence of types of Cancer in the World \cite{GLOBOCAN}}
    \label{fig:my_label}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=8cm]{Figuras/graphic2.png}
    \caption{Statistics about Incidence of types of Cancer in Brazil \cite{GLOBOCAN}}
    \label{fig:my_label}
\end{figure}

The process of the diagnosis of this type of cancer is usually made by a specialist called pathologist, who is responsible for analysing breast cells acquired through two steps: biopsy and staining. The biopsy step is a test that removes tissues or fluids from the suspicious breast area, and this procedure is the only one that can definitely define if the suspected area is cancerous or not. The staining step is responsible for add color to the cells in order to become easier the visualization of the tissue by the pathologist. After this two steps, the specialized doctor analyses the tissue through a microscope in order to determine if the there are malignant tumors or benign ones. As can be seen, the diagnosis is a really time-consuming task, which depends strongly of the expertise of the specialist. Therefore, is interesting the possibility of having applications that analyse digital images of this breast cells and be able to assist the doctor in the process of diagnosis. \par
The Digital Image Processing is the computational field responsible for dealing with this kind of task, which involves some steps for processing the image in order to achieve the better possible classification rate, in this case between malignant and benign tumors. This paper presents the steps present within of the development of an application responsible for classifying images of breast cells from features extracted, which will be described in the sequence of the paper. Some measures as accuracy, ROC Curve and AUC are compared in order to indicate the best combination of features and classifier. The rest of the paper is organized as follow:  Section II is responsible for presenting the image acquisition, while the section III demonstrates how the filtering of the images was made. Section IV presents the segmentation step, and its impact in the following phases. The step of feature extraction is presented in Section V and the feature selection in Section VI. Finishing the paper, the Section VII presents the process of classification, while Sections VIII and IX present the results and conclusion respectively.

\section{Image Acquisition}
The dataset used in this work is composed by 50 images of breast cells, being that 24 images are of malignant tumors and 26 of benign ones. Informations about this dataset can be found in \cite{artigo_database} and \href{https://bioimage.ucsb.edu/research/bio-segmentation}{\textbf{https://bioimage.ucsb.edu/research/bio-segmentation}}. The Figure 3 below presents a flowchart of the sequence of steps developed in the application.

\begin{figure}[h]
    \centering
    \includegraphics[width=8cm]{Figuras/imagem3.png}
    \caption{Flowchart of the developed method}
    \label{fig:my_label}
\end{figure}

\section{Filtering: Frequency Domain}
André: .........

\section{Segmentation}
The segmentation is an important step within the image processing, which is responsible for subdividing the an image in regions or objects that compose the signal \cite{Gonzalez:2006:DIP:1076432}, usually, this process is made through the separation of the image between background and object. Several techniques can be used in this process, such as based on thresholding, edge detection, region approaches. In this work, the optimal thresholding technique called Otsu was chosen due to its simplicity and good results. The segmentation was made after the filtering step, and the approach taken in the present work is to subtract the background of the segmented image from the original gray levels image. The code responsible for doing this task and the result produced in the image are shown in the Figure 4.

\begin{figure}[h]
    \centering
    \includegraphics[width=8cm]{Figuras/imagem_segmentacao.png}
    \caption{Segmentation of an Image of Malignant Tumor}
    \label{fig:my_label}
\end{figure}

Although visually is difficult to realize differences between the original image and the segmented one, was checked during the tests that for this image 223 682 pixels were modified in the resulted image in comparison with the original one. Since the dataset is composed for images of resolution 896x768, this quantity of modified pixels achieve around 32\% of the total.\par
Before proceeding for a description of the next steps, it is important to say that the segmentation step is not always necessary in image processing; usually, this step is applied when the following steps as feature extraction and classification are not presenting good results and it is needed to improve the process.\par
Taking this in consideration, in the next sections is presented some measures of classification for segmented and non segmented images, in order to determine the importance and necessity of this step in the whole process.

\section{Feature Extraction}
lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum,

\section{Feature Selection}
lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum,

\section{Classification}
lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum,

\section{Results}
lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum,

\section{Conclusion}
lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum,

\bibliographystyle{plain}
\bibliography{references.bib}
\end{document}

### 2019-11-18 docs/article.tex
Algumas refatorações, e inicio da escrita da parte da filtragem dentro do dominio da frequência

@@
 \title{Classification of Histopathological Images of Breast Cells between Malignant and Benign Tumors based on Handcrafted Feature Extraction}
-\author{André Furlan \& Hiago Matheus Brajato - UNESP - Universidade Estadual Paulista "Júlio de Mesquita Filho"}
+\author{Hiago Matheus Brajato \& André Furlan - UNESP - Universidade Estadual Paulista "Júlio de Mesquita Filho"}
 \date{2019-11-14}
@@
     \centering
-    \includegraphics[width=8cm]{Figuras/graphic1.png}
+    \includegraphics[width=8cm]{images/graphic1.png}
     \caption{Statistics about Incidence of types of Cancer in the World \cite{GLOBOCAN}}
@@
     \centering
-    \includegraphics[width=8cm]{Figuras/graphic2.png}
+    \includegraphics[width=8cm]{images/graphic2.png}
     \caption{Statistics about Incidence of types of Cancer in Brazil \cite{GLOBOCAN}}
@@
     \centering
-    \includegraphics[width=8cm]{Figuras/imagem3.png}
+    \includegraphics[width=8cm]{images/imagem3.png}
     \caption{Flowchart of the developed method}
@@
 \section{Filtering: Frequency Domain}
-André: .........
+The main objective of this section is separate from the noisy background the interesting areas, so the classifiers do not need to evaluate irrelevant data.
+The main idea behind it is to subtract the low frequencies components from image and, using morphological operations, remove remaining noises and close the gaps.
+\subsection{Filtering}
+Two kinds of filters were used:\\
+A low pass filter witch is used do highlight the low frequencies features of the image.In this specific case, the radius used was 60 pixels.
 
@@
     \centering
-    \includegraphics[width=8cm]{Figuras/imagem_segmentacao.png}
+    \includegraphics[width=8cm]{images/imagem_segmentacao.png}
     \caption{Segmentation of an Image of Malignant Tumor}

### 2019-11-18 src/generateMaskedImage.m

@@ -10,33 +10,33 @@ function [maskedRgbImage, mask] = generateMaskedImage(image)
 	maskedRgbImage = bsxfun(@times, image, cast(mask, 'like', image));
 	[rows, columns]= size(maskedRgbImage);
     
-    disp('Filtrando Imagens...');
+	disp('Filtrando Imagens...');
         %ch1= maskedRgbImage(:, :, 1); ch2= maskedRgbImage(:, :, 2); ch3= maskedRgbImage(:, :, 3);
         %black_pixels= ch1==0 & ch2==0 &ch3==0;
         %ch1(black_pixels)= 255; ch2(black_pixels)= 255; ch3(black_pixels)= 255; 
         %maskedRgbImage= cat(3, ch1, ch2, ch3);
-    %for i=1: rows
-     %  for j=1: columns
-        %  if maskedRgbImage(i,j)==0
-        %    maskedRgbImage(i,j)= 255;
-        %  end
-      % end
-    %end
+	%for i=1: rows
+	%  for j=1: columns
+	%  if maskedRgbImage(i,j)==0
+	%    maskedRgbImage(i,j)= 255;
+	%  end
+	% end
+	%end
 	%% Subroutines definitions
 	function [mask] = generateMask(hiFreqImage, blurred)
-			imSubtration = hiFreqImage - blurred;
+		imSubtration = hiFreqImage - blurred;
+		
+		% Binarize with Otsu
+		binarized = imbinarize(imSubtration, graythresh(imSubtration));
 			
-			% Binarize with Otsu
-			binarized = imbinarize(imSubtration, graythresh(imSubtration));
-			
-			% Morphologiacal operations for noise removal
-			se = strel ('disk',3);
-			eroded = imerode(binarized,se);
-			se = strel('disk',5);
-			expanded = im2bw(imdilate(eroded, se), 0.5);
-			
-			% Morphological operations for holes removal
-			mask = imfill(expanded,'holes');
+		% Morphologiacal operations for noise removal
+		se = strel ('disk',3);
+		eroded = imerode(binarized,se);
+		se = strel('disk',5);
+		expanded = im2bw(imdilate(eroded, se), 0.5);
+		
+		% Morphological operations for holes removal
+		mask = imfill(expanded,'holes');
 	end
 	
 	function [result] = lowOrHighPass(image, radius, sizex, sizey, highpass)

### 2019-11-18 docs/article.tex
Adicionada algumas imagens

@@
 The main objective of this section is separate from the noisy background the interesting areas, so the classifiers do not need to evaluate irrelevant data.
-The main idea behind it is to subtract the low frequencies components from image and, using morphological operations, remove remaining noises and close the gaps.
+The main idea behind it is to subtract the low frequencies components from the image and, using morphological operations, remove remaining noises and close the gaps.
 \subsection{Filtering}
 	Two kinds of filters were used:\\
-A low pass filter witch is used do highlight the low frequencies features of the image.In this specific case, the radius used was 60 pixels.
+	\par A low pass filter witch is used to highlight the low frequencies features of the image. In this specific case, the radius used was empirically determined to be 50 pixels.
 
+	\par And a high pass filter to enhance the detailed information at the image. The radius chosen this time is one.
+
+	\par To get the mask a simple subtraction operation of grayscaled lowpass filtered image from highpass filtered image is made.
+
+	\par On the resulted image, Otsu thresholding
+	operation is applied followed by two morphological operations: An erosion using a circle mask of three pixels and dilation using a circle mask of 5 pixels, these values were empirically chosen to get rid of noisy information in the image.
+
+	\par The original image, the mask, and the final masked image are shown at the \ref{fig:original}, \ref{fig:mask}, \ref{fig:maskedimage} images respectively.
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=0.7\linewidth]{images/fourrierFiltering/original}
+		\caption{Original image}
+		\label{fig:original}
+	\end{figure}
+
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=0.7\linewidth]{images/fourrierFiltering/mask}
+		\caption{Image mask generated}
+		\label{fig:mask}
+	\end{figure}
+
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=0.7\linewidth]{images/fourrierFiltering/maskedImage}
+		\caption{Imagem with mask}
+		\label{fig:maskedimage}
+	\end{figure}
 \section{Segmentation}
@@
     \caption{Segmentation of an Image of Malignant Tumor}
-    \label{fig:my_label}
+    \label{fig:imagem_segmentacao}
 \end{figure}

### 2019-11-18 docs/article.tex
Quase pronto

--- 2019-11-18 docs/article.tex
@@
 The main objective of this section is separate from the noisy background the interesting areas, so the classifiers do not need to evaluate irrelevant data.
-The main idea behind it is to subtract the low frequencies components from image and, using morphological operations, remove remaining noises and close the gaps.
-\subsection{Filtering}
-Two kinds of filters were used:\\
-A low pass filter witch is used do highlight the low frequencies features of the image.In this specific case, the radius used was 60 pixels.
+The main idea behind it is to subtract the low frequencies components from the image and, using morphological operations, remove remaining noises and close the gaps.
+\subsection{Filtering and masking}
+	Two kinds of filters were used:
+	\par A low pass filter, witch is used to highlight the low frequencies features of the image, with radius of  empirically determined 50 pixels, and a high pass filter, to enhance the detailed information at the image, with  radius of one.
 
+	\par To get the mask (figure \ref{fig:mask}) a simple subtraction operation of grayscaled lowpass filtered image from highpass filtered image is made and ,on the resulted image, Otsu thresholding operation is applied followed by three morphological operations: An erosion using a circle mask of three pixels, a dilation using a circle mask of five pixels and a hole filling; these values were empirically chosen to get rid of noisy information in the image and avoid to hide important features of the image.
+
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=0.7\linewidth]{images/fourrierFiltering/mask}
+		\caption{Image mask generated}
+		\label{fig:mask}
+	\end{figure}
+
+	\par Now that mask is ready, this one is applyed to the original image (figure \ref{fig:original}), the result of that operation is that the area with white pixels are shown and the area with black pixels are hidden (figure \ref{fig:maskedimage}).
+
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=0.7\linewidth]{images/fourrierFiltering/original}
+		\caption{Original image}
+		\label{fig:original}
+	\end{figure}
+
+	\begin{figure}[h]
+		\centering
+		\includegraphics[width=0.7\linewidth]{images/fourrierFiltering/maskedImage}
+		\caption{Image with mask}
+		\label{fig:maskedimage}
+	\end{figure}
 \section{Segmentation}

### 2019-11-18 src/generateMaskedImage.m

@@ -11,17 +11,7 @@ function [maskedRgbImage, mask] = generateMaskedImage(image)
 	[rows, columns]= size(maskedRgbImage);
     
 	disp('Filtrando Imagens...');
-        %ch1= maskedRgbImage(:, :, 1); ch2= maskedRgbImage(:, :, 2); ch3= maskedRgbImage(:, :, 3);
-        %black_pixels= ch1==0 & ch2==0 &ch3==0;
-        %ch1(black_pixels)= 255; ch2(black_pixels)= 255; ch3(black_pixels)= 255; 
-        %maskedRgbImage= cat(3, ch1, ch2, ch3);
-	%for i=1: rows
-	%  for j=1: columns
-	%  if maskedRgbImage(i,j)==0
-	%    maskedRgbImage(i,j)= 255;
-	%  end
-	% end
-	%end
+
 	%% Subroutines definitions
 	function [mask] = generateMask(hiFreqImage, blurred)
 		imSubtration = hiFreqImage - blurred;
@@ -29,7 +19,7 @@ function [maskedRgbImage, mask] = generateMaskedImage(image)
 		% Binarize with Otsu
 		binarized = imbinarize(imSubtration, graythresh(imSubtration));
 			
-		% Morphologiacal operations for noise removal
+		% Morphological operations for noise removal
 		se = strel ('disk',3);
 		eroded = imerode(binarized,se);
 		se = strel('disk',5);

### 2019-11-18 docs/article.tex
Limpeza de leve

@@
 \section{Introduction}
-Breast Cancer is a kind of malignant tumor in which cells in the breast grow out of control.
+\par Breast Cancer is a kind of malignant tumor in which cells in the breast grow out of control.
 In a recent survey called GLOBOCAN \cite{GLOBOCAN} published in 2018 by the IARC, can be visualized the statistics about this type of cancer around the world.
@@
     \caption{Statistics about Incidence of types of Cancer in Brazil \cite{GLOBOCAN}}
-    \label{fig:my_label}
+    \label{fig:graphic2}
 \end{figure}
 
-The process of the diagnosis of this type of cancer is usually made by a specialist called pathologist, who is responsible for analysing breast cells acquired through two steps: biopsy and staining.
+\par The process of the diagnosis of this type of cancer is usually made by a specialist called pathologist, who is responsible for analysing breast cells acquired through two steps: biopsy and staining.
 The biopsy step is a test that removes tissues or fluids from the suspicious breast area, and this procedure is the only one that can definitely define if the suspected area is cancerous or not.
@@
 Therefore, is interesting the possibility of having applications that analyse digital images of this breast cells and be able to assist the doctor in the process of diagnosis.
-\par
-The Digital Image Processing is the computational field responsible for dealing with this kind of task, which involves some steps for processing the image in order to achieve the better possible classification rate, in this case between malignant and benign tumors.
+
+\par The Digital Image Processing is the computational field responsible for dealing with this kind of task, which involves some steps for processing the image in order to achieve the better possible classification rate, in this case between malignant and benign tumors.
 This paper presents the steps present within of the development of an application responsible for classifying images of breast cells from features extracted, which will be described in the sequence of the paper.
@@
 \section{Image Acquisition}
-The dataset used in this work is composed by 50 images of breast cells, being that 24 images are of malignant tumors and 26 of benign ones.
+\par The used dataset in this work is composed by 50 images of breast cells, being that 24 images are of malignant tumors and 26 of benign ones.
 Informations about this dataset can be found in \cite{artigo_database} and \href{https://bioimage.ucsb.edu/research/bio-segmentation}{\textbf{https://bioimage.ucsb.edu/research/bio-segmentation}}.
@@
 \section{Filtering: Frequency Domain}
-The main objective of this section is separate from the noisy background the interesting areas, so the classifiers do not need to evaluate irrelevant data.
+\par The main objective of this section is separate from the noisy background the interesting areas, so the classifiers do not need to evaluate irrelevant data.
 The main idea behind it is to subtract the low frequencies components from the image and, using morphological operations, remove remaining noises and close the gaps.
@@
 \section{Segmentation}
-The segmentation is an important step within the image processing, which is responsible for subdividing the an image in regions or objects that compose the signal \cite{Gonzalez:2006:DIP:1076432}, usually, this process is made through the separation of the image between background and object.
+\par The segmentation is an important step within the image processing, which is responsible for subdividing the an image in regions or objects that compose the signal \cite{Gonzalez:2006:DIP:1076432}, usually, this process is made through the separation of the image between background and object.
 Several techniques can be used in this process, such as based on thresholding, edge detection, region approaches.
@@
 
-Although visually is difficult to realize differences between the original image and the segmented one, was checked during the tests that for this image 223 682 pixels were modified in the resulted image in comparison with the original one.
-Since the dataset is composed for images of resolution 896x768, this quantity of modified pixels achieve around 32\% of the total.\par
-Before proceeding for a description of the next steps, it is important to say that the segmentation step is not always necessary in image processing; usually, this step is applied when the following steps as feature extraction and classification are not presenting good results and it is needed to improve the process.\par
+\par Although visually is difficult to realize differences between the original image and the segmented one, was checked during the tests that for this image 223 682 pixels were modified in the resulted image in comparison with the original one.
+Since the dataset is composed for images of resolution 896x768, this quantity of modified pixels achieve around 32\% of the total.
+
+\par Before proceeding for a description of the next steps, it is important to say that the segmentation step is not always necessary in image processing; usually, this step is applied when the following steps as feature extraction and classification are not presenting good results and it is needed to improve the process.\par
 Taking this in consideration, in the next sections is presented some measures of classification for segmented and non segmented images, in order to determine the importance and necessity of this step in the whole process.

### 2019-11-18 src/runExample.m

@@ -1,9 +1,0 @@
-function runExample(image)
-	%% Generate masked image
-	[maskedRgbImage, mask] = generateMaskedImage(image);
-
-	%% Shows results
-	subplot(2,2,1),imshow(image);
-	subplot(2,2,3),imshow(maskedRgbImage);
-	subplot(2,2,4),imshow(mask);
-end

### 2019-11-19 docs/article.tex
feature extraction, feature selection and classification sections written

@@
 
-	\par Now that mask is ready, this one is applyed to the original image (figure \ref{fig:original}), the result of that operation is that the area with white pixels are shown and the area with black pixels are hidden (figure \ref{fig:maskedimage}).
+	\par Now that mask is ready, this one is applied to the original image (figure \ref{fig:original}), the result of that operation is that the area with white pixels are shown and the area with black pixels are hidden (figure \ref{fig:maskedimage}).
 
@@
 \section{Feature Extraction}
-lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum,
+The Feature Extraction can be considered as one of the most important steps in Image Processing: this is the last phase before the classification of the samples.
+So, the main objective here is to compose feature vectors capable to describe the samples, in order to classify correctly each example in its real class.\par
+Commonly, two approaches can be chosen in order to extract descriptors from an image: Handcrafted Features and Non-Handcrafted ones.
+The Handcrafted Features, as the name claims, are the descriptors extracted manually, according to choice of the developer, while the Non-Handcrafted Features are extracted in an automatic way, in order to do the best possible classification (one example of this approach are the Convolutional Neural Networks - CNN).
+\par
+As mentioned in the title of this paper, the used approach for extracting the descriptors from the histopathological images was the handcrafted one, where 11 descriptors were extracted and used as the input of the classifiers.
+It is important to remember that the extraction was accomplished from segmented images and non-segmented ones, so, it is possible to compare the impact of the segmentation step during the classification.
+Below is presented the extracted features used in the process.\par
+The descriptors used in the present process can be divided into 3 categories: First Order Measures, Second Order Measures and Others.
+The First Order Measures are the descriptors that consider just the gray level information about the pixels, not considering the spatial relation among them.
+The Second Order Measures, instead of the first ones, consider the spatial relation among the pixels, beyond the gray level property.
+These descriptors are extracted from the called Gray Level Co-occurrence Matrix (GLCM), that is responsible to store the frequency that a pixel with gray level \textbf{i} and other with gray level \textbf{j} occur in the image, separated for a distance \textbf{d}, in the direction\textbf{ $\theta$} \cite{conci2008computacao}.
+This method was proposed in 1973 by \cite{haralick:smc1973}, and the descriptors extracted from the GLCM are called Haralick descriptors (in the present work 6 of the 14 descriptors proposed by Haralick were used).\par
+The Others Group mentioned in the paragraph above includes the descriptors that do not fit the First and Second Measures, so, becomes important to explain how these descriptors were extracted in the proposed method.
+Three descriptors can be found in this last group: Fourier Descriptors, Local Binary Pattern Features and Fractal Dimension Descriptors.
+\par
+The Fourier Descriptors (FD), as the name say, are the features extracted from the Fourier Transform, that is responsible to transform the visualization of the signal from the spatial domain to the frequency domain, in order to become possible to see the frequencies that compose the image.
+Different approaches can be chosen to extract the FD`s, in the present work the proposed process was as follows:
+\begin{itemize}
+    \item The image was transformed to the frequency domain with the Fast Fourier Transform (FFT).
+    \item Without doing the shift of the transformed, a number of N coefficients in the middle of the spectrum were taken, so just the high frequencies was caught from the FFT.
+Doing this process, it is possible to reconstruct the image just with these high frequencies coefficients, that represent the edges inside the signal.
+In the Figure 8 it is possible to see the original image and the reconstructed one made from the descriptors.
+    \item Lastly, the complex magnitude was computed for the coefficients.
+\end{itemize}{}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=8cm]{images/imagem_reconstrucao.png}
+    \caption{Original Image and its reconstruction using the Fourier Descriptors}
+    \label{fig:my_label}
+\end{figure}{}
+The Local Binary Pattern Features (LBP) was described in \cite{lbp-OjalaPH96}, being a two-level version of the Texture Unit model proposed by \cite{Wang:1990:TCU:83597.83606}.
+The main idea is describe the image considering a neighborhood of 3x3 pixels and comparing the gray levels.\par
+The Fractal Dimension Descriptors extracted in the present work were obtained using the Box Counting Theorem, a method where the image is divided into N windows second a certain scale and the number of boxes that contains objects are counted.
+Doing this, it is possible to obtain the Fractal Dimension from each scale, as well as a General one calculated through the angular coefficient.\par
+The Figure 9 summarizes the descriptors obtained in the present work. 
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=8.5cm]{images/table_descriptors.png}
+    \caption{Descriptors}
+    \label{fig:my_label}
+\end{figure}{}
 
 \section{Feature Selection}
-lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum,
+The feature vector composed in the last step is formed by all descriptors presented in Figure 9, but it is not a good idea providing the feature vectors with all attributes as input to the classifiers, because the probability of the classification does not achieve good results is large doing the process in this way.
+This can be explained from the problem so-called "Curse of Dimensionality": after a certain number of descriptors, increasing the length of the feature vector with more attributes can degrade the performance of the classifiers.\par
+In order to obtain the more relevant descriptors and the best number of attributes, the feature vector with 7175 descriptors was examined by the ReliefF method, which is responsible for ranking the importance of the predictors based on its capability of distinguishing samples of different classes.
+The next section presents the analysis made by the ReliefF, taking into consideration the performance of the classifiers.
 
 \section{Classification}
-lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum,
+The relevance of the descriptors, as well the performance of the classifiers were measured by the analysis of ROC Curve and area under curve ROC (AUC).
+This measures were used in the proposed method because the malignant an benign classes are unbalanced in dataset, being that there are 24 malignant samples and 26 benign ones.
+Taking this is consideration, it is not a good idea analysing the obtained results through measures as accuracy, because the calculation of this last measure does not take the class balancing into consideration.\par
+The ROC Curve and AUC allow to analyse the performance of the classifiers through the confusion matrix obtained varying the threshold, so the plotted graph is formed by the X axis (1 - Specificity) and Y (Sensitivity), therefore, the AUC with value equals to 1 represents a perfect classification, while an AUC equals to 0.5 or less represents a random classification.\par
+The performance of the proposed method was evaluated through the classifiers \textbf{Discriminant Analysis}, \textbf{Decision Tree} and \textbf{Naive Bayes}, taking into consideration that all of these classifiers were submitted to the K-Folds validation method, with K equals to 5.\par
+The best number of descriptors found by testing the classifiers used in the present method can be seen in the Figure 10, which shows the number of descriptors used for the classification in X axis, and the average rates for AUC in the Y axis.\par
+It is important to remember that the graph contained in the Figure 10 was obtained using the segmented images in the process; the best number of descriptors obtained (35) was also tested in the same process without the segmentation step, in order to determine the importance of this phase in the whole process.
+The AUC rates obtained for the Discriminant Analysis, Decision Tree and Naive Bayes were 0.83, 0.66 and 0.75 respectively, resulting in an average of 0.746, well below the value showed in the graph (0.823).
+This information show us that the segmentation step produces a significant improvement in the performance of the classifiers, being necessary use its during the proposed method.
+
+\begin{figure*}[h]
+    \centering
+    \includegraphics[width=18.3cm]{images/chart.png}
+    \caption{Average rates for AUC varying the number of descriptors taking into consideration the classifiers: Decision Tree, Discriminant Analysis and Naive Bayes}
+    \label{fig:my_label}
+\end{figure*}{}
 

### 2019-11-21 src/application.m
Using a relative path for the folders

@@ -1,6 +1,6 @@
 %calling the function for reading the folder of images
-maligna_images= image_reader('D:\Hiago\Acadêmico\PÓS GRADUAÇÃO\Disciplinas\2º SEMESTRE - 2019\Processamento de Imagens Digitais\Trabalhos\Aplicação (Artigo)\Roi_Recort_bisque_Maligna');
-benigna_images= image_reader('D:\Hiago\Acadêmico\PÓS GRADUAÇÃO\Disciplinas\2º SEMESTRE - 2019\Processamento de Imagens Digitais\Trabalhos\Aplicação (Artigo)\Roi_Recort_bisque_Benigna');
+maligna_images= image_reader('.\samples\Roi_Recort_bisque_Maligna');
+benigna_images= image_reader('.\samples\Roi_Recort_bisque_Benigna');
 
 %filtering the images (choose % of the total) -- 1 == all images
 maligna_images= filtering_images(maligna_images, 1);

### 2019-11-21 src/application.m
Created all images from results

@@ -53,9 +53,23 @@ for x=1: length(feature_matrix)
     end
 end    
 
-%do the classification with the cutted_feature_matrix - I can choose the classifier at the 3º parameter
-[accuracy, matrix_of_conf]= classification_Kfolds(cutted_feature_matrix, label_matrix, 'decision_tree');
 disp('FINALIZADO - RESULTADOS----------------------------------------------');
+
+%do the classification with the cutted_feature_matrix - I can choose the classifier at the 3º parameter
+[accuracy, matrix_of_conf]= classification_Kfolds(cutted_feature_matrix, label_matrix, 'discrim_analysis');
 fprintf('Acurácia média de classificação: %f\n', accuracy);
 %plotting the returned confusion matrix 
 plot_result_matrix(matrix_of_conf, {'Maligna', 'Benigna'});
+
+%do the classification with the cutted_feature_matrix - I can choose the classifier at the 3º parameter
+[accuracy, matrix_of_conf]= classification_Kfolds(cutted_feature_matrix, label_matrix, 'decision_tree');
+fprintf('Acurácia média de classificação: %f\n', accuracy);
+%plotting the returned confusion matrix 
+plot_result_matrix(matrix_of_conf, {'Maligna', 'Benigna'});
+
+%do the classification with the cutted_feature_matrix - I can choose the classifier at the 3º parameter
+[accuracy, matrix_of_conf]= classification_Kfolds(cutted_feature_matrix, label_matrix, 'naive_bayes');
+fprintf('Acurácia média de classificação: %f\n', accuracy);
+%plotting the returned confusion matrix 
+plot_result_matrix(matrix_of_conf, {'Maligna', 'Benigna'});
+

### 2019-11-22 docs/article.tex
Figures update

@@
 \title{Classification of Histopathological Images of Breast Cells between Malignant and Benign Tumors based on Handcrafted Feature Extraction}
-\author{Hiago Matheus Brajato \& André Furlan - UNESP - Universidade Estadual Paulista "Júlio de Mesquita Filho"}
+\author{Hiago Matheus Brajato \& Andr√© Furlan - UNESP - Universidade Estadual Paulista "J√∫lio de Mesquita Filho"}
 \date{2019-11-14}
@@
 This measures were used in the proposed method because the malignant an benign classes are unbalanced in dataset, being that there are 24 malignant samples and 26 benign ones.
-Taking this is consideration, it is not a good idea analysing the obtained results through measures as accuracy, because the calculation of this last measure does not take the class balancing into consideration.\par
+Taking this is consideration, it is not a good idea analyzing the obtained results through measures as accuracy, because the calculation of this last measure does not take the class balancing into consideration.\par
 The ROC Curve and AUC allow to analyse the performance of the classifiers through the confusion matrix obtained varying the threshold, so the plotted graph is formed by the X axis (1 - Specificity) and Y (Sensitivity), therefore, the AUC with value equals to 1 represents a perfect classification, while an AUC equals to 0.5 or less represents a random classification.\par
@@
 \section{Results}
+
+discrim analysis
+decision tree
+naive bayes
+
+Acur√°cia m√©dia de classifica√ß√£o: 0.763232
+Acur√°cia m√©dia de classifica√ß√£o: 0.720606
+Acur√°cia m√©dia de classifica√ß√£o: 0.676566
+
+Acur·cia mÈdia de classificaÁ„o: 0.781414
+Acur·cia mÈdia de classificaÁ„o: 0.654343
+Acur·cia mÈdia de classificaÁ„o: 0.714747
+
 lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum,

### 2019-11-22 src/application.m

@@ -43,7 +43,7 @@ end
 %calling RELIEF for ranking the most important descriptors
 [rank, weights]= relieff(feature_matrix, label_matrix, 10);
 %selecting the first X better descriptors
-number_of_descriptors=30; 
+number_of_descriptors=35; 
 cutted_feature_matrix= zeros(rows, number_of_descriptors);
 idx_best_descriptors=1;
 for x=1: length(feature_matrix)

### 2019-11-22 src/application.m
Now each result has your own window

@@ -72,4 +72,3 @@ plot_result_matrix(matrix_of_conf, {'Maligna', 'Benigna'});
 fprintf('Acurácia média de classificação: %f\n', accuracy);
 %plotting the returned confusion matrix 
 plot_result_matrix(matrix_of_conf, {'Maligna', 'Benigna'});
-

### 2019-11-22 src/classification_Kfolds.m

@@ -46,7 +46,7 @@ function [average_accuracy, total_confusion_matrix]= classification_Kfolds(featu
     average_AUC= mean(AUCroc_per_fold);
 
     %plotting the graph of ROC Curves
-    figure(1); plot(intervals, mean_curve, 'Color', 'Black', 'LineWidth', 3.0); 
+    figure; plot(intervals, mean_curve, 'Color', 'Black', 'LineWidth', 3.0); 
     legends{k+1}= sprintf('AUC média dos folds = %.2f', average_AUC);
     xlabel('1 - Especificidade'); ylabel('Sensibilidade'); title(strcat('Curva ROC: ', classifier)); 
     legend(legends, 'Location', 'SE');

### 2019-11-22 src/plot_result_matrix.m

@@ -1,7 +1,7 @@
 function []= plot_result_matrix(input_matrix, input_labels)
 
     [rows, columns]= size(input_matrix);
-    figure(2); imagesc(input_matrix); title('Matriz de Confusão'); xlabel('Predicted Class'); ylabel('True Class');
+    figure; imagesc(input_matrix); title('Matriz de Confusão'); xlabel('Predicted Class'); ylabel('True Class');
     set(gca, 'XTick', 1:rows, 'XTickLabel', input_labels, 'YTick', 1:columns, 'YTickLabel', input_labels);
     for ii= 1: rows
         for jj=1: columns

### 2019-11-22 docs/article.tex
Some corrections

--- 2019-11-19 docs/article.tex
@@
 \section{Segmentation}
-\par The segmentation is an important step within the image processing, which is responsible for subdividing the an image in regions or objects that compose the signal \cite{Gonzalez:2006:DIP:1076432}, usually, this process is made through the separation of the image between background and object.
+\par The segmentation is an important step within the image processing, which is responsible for subdividing  an image in regions or objects that compose the signal \cite{Gonzalez:2006:DIP:1076432}, usually, this process is made through the separation of the image between background and object.
 Several techniques can be used in this process, such as based on thresholding, edge detection, region approaches.
@@
 This method was proposed in 1973 by \cite{haralick:smc1973}, and the descriptors extracted from the GLCM are called Haralick descriptors (in the present work 6 of the 14 descriptors proposed by Haralick were used).\par
-The Others Group mentioned in the paragraph above includes the descriptors that do not fit the First and Second Measures, so, becomes important to explain how these descriptors were extracted in the proposed method.
+The ther group mentioned in the paragraph above includes the descriptors that do not fit the First and Second Measures, so, becomes important to explain how these descriptors were extracted in the proposed method.
 Three descriptors can be found in this last group: Fourier Descriptors, Local Binary Pattern Features and Fractal Dimension Descriptors.
@@
 The main idea is describe the image considering a neighborhood of 3x3 pixels and comparing the gray levels.\par
-The Fractal Dimension Descriptors extracted in the present work were obtained using the Box Counting Theorem, a method where the image is divided into N windows second a certain scale and the number of boxes that contains objects are counted.
+The Fractal Dimension Descriptors extracted in the present work were obtained using the Box Counting Theorem, a method where the image is divided into N windows according to a certain scale and the number of boxes that contains the objects that must be counted.
 Doing this, it is possible to obtain the Fractal Dimension from each scale, as well as a General one calculated through the angular coefficient.\par
@@
 The relevance of the descriptors, as well the performance of the classifiers were measured by the analysis of ROC Curve and area under curve ROC (AUC).
-This measures were used in the proposed method because the malignant an benign classes are unbalanced in dataset, being that there are 24 malignant samples and 26 benign ones.
+This measures were used in the proposed method because the malignant an benign classes are unbalanced in dataset, considering that there are 24 malignant samples and 26 benign ones.
 Taking this is consideration, it is not a good idea analysing the obtained results through measures as accuracy, because the calculation of this last measure does not take the class balancing into consideration.\par
@@
 \section{Results}
+	\par The classifiers used 
+discrim analysis
+decision tree
+naive bayes
+
+Acurácia média de classificação: 0.763232
+Acurácia média de classificação: 0.720606
+Acurácia média de classificação: 0.676566
 lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum,

### 2019-11-22 docs/article.tex

@@
 \section{Results}
-	\par The classifiers used 
-discrim analysis
-decision tree
-naive bayes
 
-Acurácia média de classificação: 0.763232
-Acurácia média de classificação: 0.720606
-Acurácia média de classificação: 0.676566
 lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum,

### 2019-11-23 src/application.m
Some test..

@@ -54,21 +54,42 @@ for x=1: length(feature_matrix)
 end    
 
 disp('FINALIZADO - RESULTADOS----------------------------------------------');
+%loads the kfold separation previously generated just for the sake of reproducibility
+%if you want a new kfold separation delete the "kfold.mat" file
+k=5;
+kfolds=0;
+
+if exist('kfold.mat', 'file')
+	file = load('kfold.mat','kfolds');
+	kfolds= file.kfolds;
+else
+	kfolds= crossvalind('kfold', label_matrix, k); %creating the indices of the folds
+	save('kfold.mat','kfolds');
+end
+
+
+
+
+
+
+
+
+
 
 %do the classification with the cutted_feature_matrix - I can choose the classifier at the 3º parameter
-[accuracy, matrix_of_conf]= classification_Kfolds(cutted_feature_matrix, label_matrix, 'discrim_analysis');
+[accuracy, matrix_of_conf]= classification_Kfolds(cutted_feature_matrix, label_matrix, 'discrim_analysis', kfolds);
 fprintf('Acurácia média de classificação: %f\n', accuracy);
 %plotting the returned confusion matrix 
 plot_result_matrix(matrix_of_conf, {'Maligna', 'Benigna'});
 
 %do the classification with the cutted_feature_matrix - I can choose the classifier at the 3º parameter
-[accuracy, matrix_of_conf]= classification_Kfolds(cutted_feature_matrix, label_matrix, 'decision_tree');
+[accuracy, matrix_of_conf]= classification_Kfolds(cutted_feature_matrix, label_matrix, 'decision_tree', kfolds);
 fprintf('Acurácia média de classificação: %f\n', accuracy);
 %plotting the returned confusion matrix 
 plot_result_matrix(matrix_of_conf, {'Maligna', 'Benigna'});
 
 %do the classification with the cutted_feature_matrix - I can choose the classifier at the 3º parameter
-[accuracy, matrix_of_conf]= classification_Kfolds(cutted_feature_matrix, label_matrix, 'naive_bayes');
+[accuracy, matrix_of_conf]= classification_Kfolds(cutted_feature_matrix, label_matrix, 'naive_bayes', kfolds);
 fprintf('Acurácia média de classificação: %f\n', accuracy);
 %plotting the returned confusion matrix 
 plot_result_matrix(matrix_of_conf, {'Maligna', 'Benigna'});

### 2019-11-23 src/classification_Kfolds.m

@@ -1,16 +1,17 @@
-function [average_accuracy, total_confusion_matrix]= classification_Kfolds(feature_vectors_matrix, label_matrix, classifier)
+function [average_accuracy, total_confusion_matrix]= classification_Kfolds(feature_vectors_matrix, label_matrix, classifier, kfolds)
 %validation of the classifiers using the K-FOLDS method
 
-    k=5;
-    indexes= crossvalind('kfold', label_matrix, k); %creating the indices of the folds
-    accuracy_per_fold= zeros(1, k); total_confusion_matrix= zeros(2, 2); AUCroc_per_fold= zeros(1, k);
+	k= size(kfolds); 
+	k=k(1);
+	
+	accuracy_per_fold= zeros(1, k); total_confusion_matrix= zeros(2, 2); AUCroc_per_fold= zeros(1, k);
     %for ROC Curves and Average ROC Curve
     legends= cell(1, k+1);  intervals= linspace(0, 1, 100);  
     
     %beginning of the loop for folds
     for i=1: k
-       idx_test= (indexes==i);
-       idx_train= (indexes~=i);
+       idx_test= (kfolds==i);
+       idx_train= (kfolds~=i);
        classes_of_test= label_matrix(idx_test, :); %for comparating with the response of the classifier
        
        %here I am training the classifier 

### 2019-11-23 src/application.m
Create a function that loads or create kfolds

@@ -10,13 +10,13 @@ benigna_images= filtering_images(benigna_images, 1);
 gray_maligna_images= cell(1, length(maligna_images)); segmented_maligna_images= cell(1, length(maligna_images));
 gray_benigna_images= cell(1, length(benigna_images)); segmented_benigna_images= cell(1, length(benigna_images));
 for i=1: length(benigna_images)
-    if i<25
-       gray_maligna_images{i}= rgb2gray(maligna_images{i});
-       segmented_maligna_images{i}= imsubtract(gray_maligna_images{i}, uint8(imbinarize(gray_maligna_images{i})));
-    end
-    gray_benigna_images{i}= rgb2gray(benigna_images{i});
-    segmented_benigna_images{i}= imsubtract(gray_benigna_images{i}, uint8(imbinarize(gray_benigna_images{i})));
-end   
+	if i<25
+		gray_maligna_images{i}= rgb2gray(maligna_images{i});
+		segmented_maligna_images{i}= imsubtract(gray_maligna_images{i}, uint8(imbinarize(gray_maligna_images{i})));
+	end
+	gray_benigna_images{i}= rgb2gray(benigna_images{i});
+	segmented_benigna_images{i}= imsubtract(gray_benigna_images{i}, uint8(imbinarize(gray_benigna_images{i})));
+end
 
 %matrix of labels, for Relief and Classifiers
 label_matrix= cell(50,1);
@@ -26,70 +26,54 @@ formatted_feature_vector= cell2mat(feature_extractor(gray_maligna_images{1})); %
 feature_matrix= zeros(length(maligna_images)+length(benigna_images), length(formatted_feature_vector));
 [rows, columns]= size(feature_matrix); idx_bng=1;
 for i=1: rows
-    if i < (length(maligna_images)+1) %here I can choose if I want to extract from original gray images or segmented ones
-        feature_vector= feature_extractor(segmented_maligna_images{i});% <-
-        formatted_feature_vector= cell2mat(feature_vector); 
-        feature_matrix(i, 1:length(feature_matrix))= formatted_feature_vector;
-        label_matrix{i}= 'maligna';
-    else
-        feature_vector= feature_extractor(segmented_benigna_images{idx_bng});% <-
-        formatted_feature_vector= cell2mat(feature_vector); 
-        feature_matrix(i, 1:length(feature_matrix))= formatted_feature_vector;
-        idx_bng= idx_bng+1;
[…]

### 2019-11-23 src/classification_Kfolds.m

@@ -1,15 +1,15 @@
-function [average_accuracy, total_confusion_matrix]= classification_Kfolds(feature_vectors_matrix, label_matrix, classifier, kfolds)
+function [average_accuracy, total_confusion_matrix]= classification_Kfolds(feature_vectors_matrix, label_matrix, classifier, kfoldsAmount)
 %validation of the classifiers using the K-FOLDS method
 
-	k= size(kfolds); 
-	k=k(1);
-	
-	accuracy_per_fold= zeros(1, k); total_confusion_matrix= zeros(2, 2); AUCroc_per_fold= zeros(1, k);
+	accuracy_per_fold= zeros(1, kfoldsAmount); total_confusion_matrix= zeros(2, 2); AUCroc_per_fold= zeros(1, kfoldsAmount);
     %for ROC Curves and Average ROC Curve
-    legends= cell(1, k+1);  intervals= linspace(0, 1, 100);  
+    legends= cell(1, kfoldsAmount+1);  intervals= linspace(0, 1, 100);  
     
     %beginning of the loop for folds
-    for i=1: k
+    for i=1: kfoldsAmount
+		
+		fprintf('Iteração: %f', i);
+		
        idx_test= (kfolds==i);
        idx_train= (kfolds~=i);
        classes_of_test= label_matrix(idx_test, :); %for comparating with the response of the classifier
@@ -36,9 +36,9 @@ function [average_accuracy, total_confusion_matrix]= classification_Kfolds(featu
        %for getting an average of the ROC curves from each fold
        x_adj= adjust_unique_points(Xroc); %interp1 requires unique points
        if i==1
-           mean_curve= (interp1(x_adj, Yroc, intervals))/k; 
+           mean_curve= (interp1(x_adj, Yroc, intervals))/kfoldsAmount; 
        else
-           mean_curve= mean_curve+ (interp1(x_adj, Yroc, intervals))/k; 
+           mean_curve= mean_curve+ (interp1(x_adj, Yroc, intervals))/kfoldsAmount; 
        end
        
     end %end of the loop
@@ -48,7 +48,7 @@ function [average_accuracy, total_confusion_matrix]= classification_Kfolds(featu
 
     %plotting the graph of ROC Curves
     figure; plot(intervals, mean_curve, 'Color', 'Black', 'LineWidth', 3.0); 
-    legends{k+1}= sprintf('AUC média dos folds = %.2f', average_AUC);
[…]

### 2019-11-23 src/loadOrCreateKfolds.m

@@ -1,0 +1,13 @@
+function [ kfolds ] = loadOrCreateKfolds( amount )
+	%LOADORCREATEKFOLDS Load existing k folds or create one
+	% Loads the kfold separation previously generated just for the sake of reproducibility.
+	% If you want a new kfold separation delete the "kfold.mat" file
+	if exist('kfold.mat', 'file')
+		file = load('kfold.mat','kfolds');
+		kfolds= file.kfolds;
+	else
+		kfolds= crossvalind('kfold', label_matrix, k); %creating the indices of the folds
+		save('kfold.mat','kfolds');
+	end
+end
+

### 2019-11-23 src/classification_Kfolds.m
Solving ssome bugs

@@ -1,4 +1,4 @@
-function [average_accuracy, total_confusion_matrix]= classification_Kfolds(feature_vectors_matrix, label_matrix, classifier, kfoldsAmount)
+function [average_accuracy, total_confusion_matrix]= classification_Kfolds(feature_vectors_matrix, label_matrix, classifier, kfolds, kfoldsAmount)
 %validation of the classifiers using the K-FOLDS method
 
 	accuracy_per_fold= zeros(1, kfoldsAmount); total_confusion_matrix= zeros(2, 2); AUCroc_per_fold= zeros(1, kfoldsAmount);

### 2019-11-23 src/loadOrCreateKfolds.m

@@ -5,6 +5,11 @@ function [ kfolds ] = loadOrCreateKfolds( amount )
 	if exist('kfold.mat', 'file')
 		file = load('kfold.mat','kfolds');
 		kfolds= file.kfolds;
+		
+		if max(kfolds) < amount
+			kfolds= crossvalind('kfold', label_matrix, k); %creating the indices of the folds
+			save('kfold.mat','kfolds');	
+		end
 	else
 		kfolds= crossvalind('kfold', label_matrix, k); %creating the indices of the folds
 		save('kfold.mat','kfolds');

### 2019-11-23 src/adjust_unique_points.m
Better status messages. Warnings removed. Better indentation.

@@ -1,12 +1,11 @@
 function x= adjust_unique_points(Xroc)
-
-    x= zeros(1, length(Xroc));
-    aux= 0.0001;
-    for i=1: length(Xroc)
-        if i~=1
-            x(i)= Xroc(i)+aux;
-            aux= aux+0.0001;
-        end
-        
-    end
+	x= zeros(1, length(Xroc));
+	aux= 0.0001;
+	for i=1: length(Xroc)
+		if i~=1
+			x(i)= Xroc(i)+aux;
+			aux= aux+0.0001;
+		end
+		
+	end
 end

### 2019-11-23 src/application.m

@@ -1,3 +1,5 @@
+kfoldsAmount=5;
+
 %calling the function for reading the folder of images
 maligna_images= image_reader('.\samples\Roi_Recort_bisque_Maligna');
 benigna_images= image_reader('.\samples\Roi_Recort_bisque_Benigna');
@@ -26,6 +28,7 @@ formatted_feature_vector= cell2mat(feature_extractor(gray_maligna_images{1})); %
 feature_matrix= zeros(length(maligna_images)+length(benigna_images), length(formatted_feature_vector));
 [rows, columns]= size(feature_matrix); idx_bng=1;
 for i=1: rows
+	fprintf('Extraindo características: Fase %d de %d...\n', i, rows);
 	if i < (length(maligna_images)+1) %here I can choose if I want to extract from original gray images or segmented ones
 		feature_vector= feature_extractor(segmented_maligna_images{i});% <-
 		formatted_feature_vector= cell2mat(feature_vector);
@@ -40,6 +43,7 @@ for i=1: rows
 	end
 end
 
+fprintf('Selecionando o melhor grupo de características\n');
 %calling RELIEF for ranking the most important descriptors
 [rank, weights]= relieff(feature_matrix, label_matrix, 10);
 %selecting the first X better descriptors
@@ -57,8 +61,7 @@ disp('FINALIZADO - RESULTADOS----------------------------------------------');
 
 % Loads the kfold separation previously generated just for the sake of reproducibility.
 % If you want a new kfold separation delete the "kfold.mat" file
-kfoldsAmount=5;
-kfolds = loadOrCreateKfolds(kfoldsAmount);
+kfolds = loadOrCreateKfolds(kfoldsAmount, label_matrix);
 
 %do the classification with the cutted_feature_matrix - I can choose the classifier at the 3º parameter
 [accuracy, matrix_of_conf]= classification_Kfolds(cutted_feature_matrix, label_matrix, 'discrim_analysis', kfolds, kfoldsAmount);

### 2019-11-23 src/classification_Kfolds.m

@@ -1,56 +1,54 @@
 function [average_accuracy, total_confusion_matrix]= classification_Kfolds(feature_vectors_matrix, label_matrix, classifier, kfolds, kfoldsAmount)
-%validation of the classifiers using the K-FOLDS method
-
+	%validation of the classifiers using the K-FOLDS method
+	
 	accuracy_per_fold= zeros(1, kfoldsAmount); total_confusion_matrix= zeros(2, 2); AUCroc_per_fold= zeros(1, kfoldsAmount);
-    %for ROC Curves and Average ROC Curve
-    legends= cell(1, kfoldsAmount+1);  intervals= linspace(0, 1, 100);  
-    
-    %beginning of the loop for folds
-    for i=1: kfoldsAmount
+	%for ROC Curves and Average ROC Curve
+	legends= cell(1, kfoldsAmount+1);  intervals= linspace(0, 1, 100);
+	
+	%beginning of the loop for folds
+	for i=1: kfoldsAmount
+		idx_test= (kfolds==i);
+		idx_train= (kfolds~=i);
+		classes_of_test= label_matrix(idx_test, :); %for comparating with the response of the classifier
 		
-		fprintf('Iteração: %f', i);
+		%here I am training the classifier
+		if strcmpi(classifier, 'discrim_analysis')
+			trained_classifier= fitcdiscr(feature_vectors_matrix(idx_train, :), label_matrix(idx_train,:), 'ClassNames', {'maligna', 'benigna'}, 'discrimType', 'diagLinear');
+		elseif strcmpi(classifier, 'decision_tree')
+			trained_classifier= fitctree(feature_vectors_matrix(idx_train, :), label_matrix(idx_train,:), 'ClassNames', {'maligna', 'benigna'});
+		elseif strcmpi(classifier, 'naive_bayes')
+			trained_classifier= fitcnb(feature_vectors_matrix(idx_train, :), label_matrix(idx_train,:), 'ClassNames', {'maligna', 'benigna'}, 'DistributionNames', 'kernel');
+		else
+			error('Classificador não disponível na função');
+		end
 		
-       idx_test= (kfolds==i);
-       idx_train= (kfolds~=i);
-       classes_of_test= label_matrix(idx_test, :); %for comparating with the response of the classifier
-       
-       %here I am training the classifier 
-       if strcmpi(classifier, 'discrim_analysis') 
[…]

### 2019-11-23 src/feature_extractor.m

@@ -1,20 +1,20 @@
 function vector= feature_extractor(input_img) %this function receives a grayscale img as input and returns a feature vector
-
-    %FIRST ORDER MEASURES
-        vector{1}= mean2(input_img);  %average
-        vector{2}= (std2(input_img))^2; %variance is the square of the standard deviation
-    %SECOND ORDER MEASURES -> derived from gray level co-ocurrence matrix (glcm)
-        glcm= graycomatrix(input_img);
-        vector{3}= graycoprops(glcm, 'energy'); vector{3}= struct2array(vector{3}); %energy from glcm
-        vector{4}= entropy(glcm); %entropy from glcm
-        vector{5}= graycoprops(glcm, 'contrast'); vector{5}= struct2array(vector{5});%constrast from glcm
-        vector{6}= (std2(glcm))^2; %heterogeneity is equals to the variance (square of standard deviation)
-        vector{7}= graycoprops(glcm, 'correlation'); vector{7}= struct2array(vector{7}); %correlation from glcm
-        vector{8}= graycoprops(glcm, 'homogeneity'); vector{8}= struct2array(vector{8});%homegenity from glcm
-    %FOURIER DESCRIPTOR -> extracted from the binary image
-        vector{9}= fourier_descriptors(input_img);
-    %LOCAL BINARY PATTERN (LBP)
-        vector{10}= double(extractLBPFeatures(input_img));  disp('Extraindo características...');
-    %FRACTAL DIMENSION -> extracted from the binary image
-        vector{11}= fract_dim_boxcounting(input_img);
+	
+	%FIRST ORDER MEASURES
+	vector{1}= mean2(input_img);  %average
+	vector{2}= (std2(input_img))^2; %variance is the square of the standard deviation
+	%SECOND ORDER MEASURES -> derived from gray level co-ocurrence matrix (glcm)
+	glcm= graycomatrix(input_img);
+	vector{3}= graycoprops(glcm, 'energy'); vector{3}= struct2array(vector{3}); %energy from glcm
+	vector{4}= entropy(glcm); %entropy from glcm
+	vector{5}= graycoprops(glcm, 'contrast'); vector{5}= struct2array(vector{5});%constrast from glcm
+	vector{6}= (std2(glcm))^2; %heterogeneity is equals to the variance (square of standard deviation)
[…]

### 2019-11-23 src/filtering_images.m

@@ -1,12 +1,13 @@
 function filtered_images= filtering_images(image_group, percentage)%this function receives a group and a percentage of
-%images that will be filtered
-
-    proportion_filtered= round(percentage * length(image_group));    
-    random_list= randperm(length(image_group), proportion_filtered);
-
-    for i=1: proportion_filtered
-        image_group{random_list(i)}= generateMaskedImage(image_group{random_list(i)});
-    end
-    
-    filtered_images= image_group;
+	%images that will be filtered
+	
+	proportion_filtered= round(percentage * length(image_group));
+	random_list= randperm(length(image_group), proportion_filtered);
+	
+	for i=1: proportion_filtered
+		fprintf('Filtrando Imagens: Fase %d de %d...\n', i, proportion_filtered);
+		image_group{random_list(i)}= generateMaskedImage(image_group{random_list(i)});
+	end
+	
+	filtered_images= image_group;
 end

### 2019-11-23 src/fourier_descriptors.m

@@ -1,21 +1,21 @@
 function vector= fourier_descriptors(input_img) %this function receives a img for calculating Fourier descriptors (FD)
-%the FD are calculated catching just the high frequencies of the DFT
-%if I catch just the coeficients above certain frequency I can reconstruct the img just with the edges
-%so, the objective is catch just the frequencies in the middle of the spectrum (without the shift)
-%figure(10); imshow(input_img); title('Imagem Original');
-
-coefficients= fft2(input_img); %dft of the image
-[rows, columns]= size(coefficients);
-
-%I want just the high frequencies, the edges of the objects -> in the center of the spectrum (10%)
-index_highrows= round(rows*0.10);
-index_highcolumns= round(columns*0.10);
-high_coef= cell(1, 1);
-high_coef{1}= coefficients(((rows/2)-(index_highrows/2)): ((rows/2)+(index_highrows/2)), ((columns/2)-(index_highcolumns/2)) : ((columns/2)+(index_highcolumns/2)));
-
-%showing the reconstruction just with the high frequencies (descriptors)
-%figure(1); imshow(log(abs(ifft2(high_coef{1}))), []); title('Imagem reconstruída com 10%'); 
-vector= abs(high_coef{1}); %getting the magnitude of complex number
-vector= reshape(vector, 1, []); %formating the response to one line to compose the final_vector
-
+	%the FD are calculated catching just the high frequencies of the DFT
+	%if I catch just the coeficients above certain frequency I can reconstruct the img just with the edges
+	%so, the objective is catch just the frequencies in the middle of the spectrum (without the shift)
+	%figure(10); imshow(input_img); title('Imagem Original');
+	
+	coefficients= fft2(input_img); %dft of the image
+	[rows, columns]= size(coefficients);
+	
+	%I want just the high frequencies, the edges of the objects -> in the center of the spectrum (10%)
+	index_highrows= round(rows*0.10);
+	index_highcolumns= round(columns*0.10);
+	high_coef= cell(1, 1);
+	high_coef{1}= coefficients(round((rows/2)-(index_highrows/2)): round((rows/2)+(index_highrows/2)), round((columns/2)-(index_highcolumns/2)) : round((columns/2)+(index_highcolumns/2)));
+	
+	%showing the reconstruction just with the high frequencies (descriptors)
+	%figure(1); imshow(log(abs(ifft2(high_coef{1}))), []); title('Imagem reconstruída com 10%');
[…]

### 2019-11-23 src/fract_dim_boxcounting.m

@@ -1,63 +1,63 @@
 function formatted_vector= fract_dim_boxcounting(input_img) %this method receives an img as input for box counting
-    input_img= imresize(input_img, [512,512]);
-    [rows, columns]= size(input_img);
-    max_scale= log2(rows); %the max number of the scale is equals to the log of the img dimension
-    fd_scale= cell(1, max_scale); %fractal dimension of each scale 
-    input_img= imbinarize(input_img);
-
-    for i=1: max_scale
-        number_of_boxes= 2^i;
-        denominator= log(number_of_boxes);
-        width_box= columns/number_of_boxes;
-        height_box= rows/number_of_boxes;
-        divide_aux= number_of_boxes;
-        number_of_boxes= number_of_boxes^2;
-        sub_images= cell(1, number_of_boxes);
-        total_boxes_with_objects= 0;
-        %now I have the number of the boxes and the size of each one -> I can count the boxes with objects
-        
-        %first, I divide the complete image into the boxes for counting
-        x=1; y=1; extra_count=1;
-        for aux_r=1: divide_aux
-            for aux_c=1: divide_aux
-              sub_images{extra_count}= input_img(x: x+height_box-1, y: y+width_box-1, :);
-              extra_count= extra_count+1;
-              y= y+width_box;
-            end
-            y=1; x=x+height_box;
-        end
-        
-        %now I can do the counting in each box
-        for j=1: number_of_boxes %for each box
-            counter_box=0;
-            for k=1: height_box %going through each box 
-                for m=1: width_box
-                    if sub_images{j}(k, m)==0 %if there is object in the box, then increments the counter_box
-                        counter_box= counter_box+1;
-                    end
-                end
-            end
-            if counter_box>0
-                total_boxes_with_objects= total_boxes_with_objects+1;
-            end
-        end    
-        nominator= log(total_boxes_with_objects);  
-        fd_scale{i}= nominator/denominator;
-        if i==1
-            delta_y= nominator; delta_x= denominator;
-        end
-        if i==max_scale
-            general_fd= ((nominator-delta_y)/(denominator-delta_x)); %general fractal dimension
-        end
-    end
-
-    vector{1}= fd_scale; 
[…]

### 2019-11-23 src/generateMaskedImage.m

@@ -9,21 +9,20 @@ function [maskedRgbImage, mask] = generateMaskedImage(image)
 	%% Final result
 	maskedRgbImage = bsxfun(@times, image, cast(mask, 'like', image));
 	[rows, columns]= size(maskedRgbImage);
-    
-	disp('Filtrando Imagens...');
-
+	
 	%% Subroutines definitions
 	function [mask] = generateMask(hiFreqImage, blurred)
 		imSubtration = hiFreqImage - blurred;
 		
 		% Binarize with Otsu
 		binarized = imbinarize(imSubtration, graythresh(imSubtration));
-			
+		
 		% Morphological operations for noise removal
 		se = strel ('disk',3);
 		eroded = imerode(binarized,se);
 		se = strel('disk',5);
-		expanded = im2bw(imdilate(eroded, se), 0.5);
+		%expanded = im2bw(imdilate(eroded, se), 0.5);
+		expanded = imdilate(eroded, se);
 		
 		% Morphological operations for holes removal
 		mask = imfill(expanded,'holes');
@@ -39,12 +38,12 @@ function [maskedRgbImage, mask] = generateMaskedImage(image)
 		else
 			c=z<=radius;
 		end
-
+		
 		%% Apply filter
 		af=fftshift(fft2(image));
 		af1=af.*c;
 		result=ifft2(ifftshift(af1));
-
+		
 		%% Normalize result
 		f1=abs(result);
 		fm=max(result(:));

### 2019-11-23 src/image_reader.m

@@ -1,11 +1,11 @@
 function array= image_reader(path)%reading all images of the folder
-    my_folder= path;
-    file_pattern= fullfile(my_folder, '*.tif');%creates a file with all images in the TIF format from the desired folder
-    list= dir(file_pattern);%list the files into the folder
-    array= cell(1, length(list)); %creates a 1D array for the size of the list
-    for i=1: length(list)
-        imgfile_name= list(i).name;
-        completefile_name= fullfile(my_folder, imgfile_name); %build a complete path from the sub-paths
-        array{i}= imread(completefile_name);
-    end     
+	my_folder= path;
+	file_pattern= fullfile(my_folder, '*.tif');%creates a file with all images in the TIF format from the desired folder
+	list= dir(file_pattern);%list the files into the folder
+	array= cell(1, length(list)); %creates a 1D array for the size of the list
+	for i=1: length(list)
+		imgfile_name= list(i).name;
+		completefile_name= fullfile(my_folder, imgfile_name); %build a complete path from the sub-paths
+		array{i}= imread(completefile_name);
+	end
 end

### 2019-11-23 src/loadOrCreateKfolds.m

@@ -1,4 +1,4 @@
-function [ kfolds ] = loadOrCreateKfolds( amount )
+function [ kfolds ] = loadOrCreateKfolds( amount, labelsMatrix )
 	%LOADORCREATEKFOLDS Load existing k folds or create one
 	% Loads the kfold separation previously generated just for the sake of reproducibility.
 	% If you want a new kfold separation delete the "kfold.mat" file
@@ -6,12 +6,12 @@ function [ kfolds ] = loadOrCreateKfolds( amount )
 		file = load('kfold.mat','kfolds');
 		kfolds= file.kfolds;
 		
-		if max(kfolds) < amount
-			kfolds= crossvalind('kfold', label_matrix, k); %creating the indices of the folds
-			save('kfold.mat','kfolds');	
+		if max(kfolds) ~= amount
+			kfolds= crossvalind('kfold', labelsMatrix, amount); %creating the indices of the folds
+			save('kfold.mat','kfolds');
 		end
 	else
-		kfolds= crossvalind('kfold', label_matrix, k); %creating the indices of the folds
+		kfolds= crossvalind('kfold', labelsMatrix, amount); %creating the indices of the folds
 		save('kfold.mat','kfolds');
 	end
 end

### 2019-11-23 src/plot_result_matrix.m

@@ -1,22 +1,22 @@
 function []= plot_result_matrix(input_matrix, input_labels)
-
-    [rows, columns]= size(input_matrix);
-    figure; imagesc(input_matrix); title('Matriz de Confusão'); xlabel('Predicted Class'); ylabel('True Class');
-    set(gca, 'XTick', 1:rows, 'XTickLabel', input_labels, 'YTick', 1:columns, 'YTickLabel', input_labels);
-    for ii= 1: rows
-        for jj=1: columns
-            text(jj, ii, num2str(input_matrix(ii, jj)), 'Color', 'white', 'FontSize', 14);    
-        end
-    end
-    
-    my_map= [0 0 0.3
-        0 0 0.4
-        0 0 0.5
-        0 0 0.6
-        0 0 0.7
-        0 0 0.8
-        0 0 0.9
-        0 0 1.0];
-    colormap(my_map);
-
+	
+	[rows, columns]= size(input_matrix);
+	figure; imagesc(input_matrix); title('Confusion Matrix'); xlabel('Predicted Class'); ylabel('True Class');
+	set(gca, 'XTick', 1:rows, 'XTickLabel', input_labels, 'YTick', 1:columns, 'YTickLabel', input_labels);
+	for ii= 1: rows
+		for jj=1: columns
+			text(jj, ii, num2str(input_matrix(ii, jj)), 'Color', 'white', 'FontSize', 14);
+		end
+	end
+	
+	my_map= [0 0 0.3
+		0 0 0.4
+		0 0 0.5
+		0 0 0.6
+		0 0 0.7
+		0 0 0.8
+		0 0 0.9
+		0 0 1.0];
+	colormap(my_map);
+	
 end

### 2019-11-23 src/application.m
More tweaks

@@ -1,3 +1,4 @@
+% If you want a new kfold separation delete the "kfold.mat" file
 kfoldsAmount=5;
 
 %calling the function for reading the folder of images
@@ -26,9 +27,9 @@ label_matrix= cell(50,1);
 %matrix of caracteristics of all images - the next two lines are just for allocation
 formatted_feature_vector= cell2mat(feature_extractor(gray_maligna_images{1})); %just for getting the length
 feature_matrix= zeros(length(maligna_images)+length(benigna_images), length(formatted_feature_vector));
-[rows, columns]= size(feature_matrix); idx_bng=1;
-for i=1: rows
-	fprintf('Extraindo características: Fase %d de %d...\n', i, rows);
+[amountOfImages, columns]= size(feature_matrix); idx_bng=1;
+for i=1: amountOfImages
+	fprintf('Extraindo características: Fase %d de %d...\n', i, amountOfImages);
 	if i < (length(maligna_images)+1) %here I can choose if I want to extract from original gray images or segmented ones
 		feature_vector= feature_extractor(segmented_maligna_images{i});% <-
 		formatted_feature_vector= cell2mat(feature_vector);
@@ -42,41 +43,24 @@ for i=1: rows
 		label_matrix{i}= 'benigna';
 	end
 end
+% The labels for final graphic
+xlabels = zeros(40,1);
 
-fprintf('Selecionando o melhor grupo de características\n');
-%calling RELIEF for ranking the most important descriptors
-[rank, weights]= relieff(feature_matrix, label_matrix, 10);
-%selecting the first X better descriptors
-number_of_descriptors=35;
-cutted_feature_matrix= zeros(rows, number_of_descriptors);
-idx_best_descriptors=1;
-for x=1: length(feature_matrix)
-	if(rank(x))<= number_of_descriptors
-		cutted_feature_matrix(1:50, idx_best_descriptors)= feature_matrix(1:50, x);
-		idx_best_descriptors= idx_best_descriptors+1;
-	end
+% The data for the final graphic
+results = zeros(40,4);
+
+[accuracy01, accuracy02, accuracy03, average] = classificationTests(feature_matrix, label_matrix, 6, kfoldsAmount, amountOfImages, true);
+
+% Evaluate data for each amount of descriptors from 1 up to 40
+for number_of_descriptors=1: 40
[…]

### 2019-11-23 src/classificationTests.m

@@ -1,0 +1,50 @@
+function [accuracy01, accuracy02, accuracy03, average] = classificationTests( feature_matrix, label_matrix, number_of_descriptors, kfoldsAmount, amountOfImages, plot )
+	%CLASSIFICATIONTESTS Summary of this function goes here
+	%   Detailed explanation goes here
+	fprintf('Selecionando o melhor grupo de características\n');
+	%calling RELIEF for ranking the most important descriptors
+	[rank, weights]= relieff(feature_matrix, label_matrix, 10);
+	cutted_feature_matrix= zeros(amountOfImages, number_of_descriptors);
+	idx_best_descriptors=1;
+	for x=1: length(feature_matrix)
+		if(rank(x))<= number_of_descriptors
+			cutted_feature_matrix(1:50, idx_best_descriptors)= feature_matrix(1:50, x);
+			idx_best_descriptors= idx_best_descriptors+1;
+		end
+	end
+	
+	fprintf('RESULTADOS [%f descritores, %d kfolds]\n', number_of_descriptors, kfoldsAmount);
+	
+	% Loads the kfold separation previously generated just for the sake of reproducibility.
+	% If you want a new kfold separation delete the "kfold.mat" file
+	kfolds = loadOrCreateKfolds(kfoldsAmount, label_matrix);
+	
+	%do the classification with the cutted_feature_matrix - I can choose the classifier at the 3º parameter
+	[accuracy01, matrix_of_conf01]= classification_Kfolds(cutted_feature_matrix, label_matrix, 'discrim_analysis', kfolds, kfoldsAmount, plot);
+	fprintf('Acurácia média de classificação para discrim_analysis:\t %f\n', accuracy01);
+	%plotting the returned confusion matrix
+	if plot
+		plot_result_matrix(matrix_of_conf01, {'Maligna', 'Benigna'});
+	end
+	
+	%do the classification with the cutted_feature_matrix - I can choose the classifier at the 3º parameter
+	[accuracy02, matrix_of_conf02]= classification_Kfolds(cutted_feature_matrix, label_matrix, 'decision_tree', kfolds, kfoldsAmount, plot);
+	fprintf('Acurácia média de classificação para decision_tree:\t %f\n', accuracy02);
+	%plotting the returned confusion matrix
+	if plot
+		plot_result_matrix(matrix_of_conf02, {'Maligna', 'Benigna'});
+	end
+	
[…]

### 2019-11-23 src/classification_Kfolds.m

@@ -1,4 +1,4 @@
-function [average_accuracy, total_confusion_matrix]= classification_Kfolds(feature_vectors_matrix, label_matrix, classifier, kfolds, kfoldsAmount)
+function [average_accuracy, total_confusion_matrix]= classification_Kfolds(feature_vectors_matrix, label_matrix, classifier, kfolds, kfoldsAmount, plot)
 	%validation of the classifiers using the K-FOLDS method
 	
 	accuracy_per_fold= zeros(1, kfoldsAmount); total_confusion_matrix= zeros(2, 2); AUCroc_per_fold= zeros(1, kfoldsAmount);
@@ -29,7 +29,10 @@ function [average_accuracy, total_confusion_matrix]= classification_Kfolds(featu
 		
 		%ROC Curve and AUC (plotting the ROC Curve for each fold and an average of the folds)
 		[Xroc, Yroc, ~, AUCroc_per_fold(i)]= perfcurve(label_matrix(idx_test, :), scores(:, 1), 'maligna');
-		plot(Xroc, Yroc, 'LineWidth', 1.5); legends{i}= sprintf('fold %d (AUC = %.2f)', i, AUCroc_per_fold(i));
+		
+		if plot
+			plot(Xroc, Yroc, 'LineWidth', 1.5); legends{i}= sprintf('fold %d (AUC = %.2f)', i, AUCroc_per_fold(i));
+		end
 		
 		%for getting an average of the ROC curves from each fold
 		x_adj= adjust_unique_points(Xroc); %interp1 requires unique points
@@ -45,10 +48,12 @@ function [average_accuracy, total_confusion_matrix]= classification_Kfolds(featu
 	average_AUC= mean(AUCroc_per_fold);
 	
 	%plotting the graph of ROC Curves
-	hold on;
-	figure; plot(intervals, mean_curve, 'Color', 'Black', 'LineWidth', 3.0);
-	legends = sprintf('Average folds AUC= %.2f', average_AUC);
-	xlabel('1 - Specificity'); ylabel('Sensitivity'); title(strcat('ROC curve: ', classifier));
-	legend(legends, 'Location', 'SE');
-	hold off;
+	if plot
+		hold on;
+		figure; plot(intervals, mean_curve, 'Color', 'Black', 'LineWidth', 3.0);
+		legends = sprintf('Average folds AUC= %.2f', average_AUC);
[…]

### 2019-11-23 src/plotFinalResults.m

@@ -1,0 +1,36 @@
+function plotFinalResults(xlabels, results)
+	%plotFinalResults(xlabels, results)
+	%  xlabels:  vector of x axes labels
+	%  results:  matrix of y data
+	
+	% Create figure
+	figure1 = figure;
+
+	% Create axes
+	axes1 = axes('Parent',figure1);
+	hold(axes1,'on');
+	
+	% Create multiple lines using matrix input to plot
+	plot1 = plot(xlabels,results,'LineWidth',2,'Parent',axes1);
+	set(plot1(1),'DisplayName','Average acuracy','Marker','diamond',...
+		'Color',[1 0 0]);
+	set(plot1(2),'DisplayName','discrim\_analysis','LineWidth',0.5);
+	set(plot1(3),'DisplayName','decision\_tree','LineStyle',':');
+	set(plot1(4),'DisplayName','naive\_bayes','LineStyle','-.');
+	
+	% Create xlabel
+	xlabel('Number of descriptors','FontSize',13.2);
+	
+	% Create title
+	title('Accuracy of classifiers according to the number of descriptors',...
+		'FontSize',13.2);
+	
+	% Create ylabel
+	ylabel('Acuracy','FontSize',13.2);
+	
+	% Set the remaining axes properties
+	set(axes1,'FontSize',12,'XGrid','on','YGrid','on');
+	% Create legend
+	legend1 = legend(axes1,'show');
+	set(legend1,'FontSize',10.8);
+end

### 2019-11-23 src/classificationTests.m
A bug on plotting is solved

@@ -1,4 +1,4 @@
-function [accuracy01, accuracy02, accuracy03, average] = classificationTests( feature_matrix, label_matrix, number_of_descriptors, kfoldsAmount, amountOfImages, plot )
+function [accuracy01, accuracy02, accuracy03, average] = classificationTests( feature_matrix, label_matrix, number_of_descriptors, kfoldsAmount, amountOfImages, plotIt )
 	%CLASSIFICATIONTESTS Summary of this function goes here
 	%   Detailed explanation goes here
 	fprintf('Selecionando o melhor grupo de características\n');
@@ -20,26 +20,26 @@ function [accuracy01, accuracy02, accuracy03, average] = classificationTests( fe
 	kfolds = loadOrCreateKfolds(kfoldsAmount, label_matrix);
 	
 	%do the classification with the cutted_feature_matrix - I can choose the classifier at the 3º parameter
-	[accuracy01, matrix_of_conf01]= classification_Kfolds(cutted_feature_matrix, label_matrix, 'discrim_analysis', kfolds, kfoldsAmount, plot);
+	[accuracy01, matrix_of_conf01]= classification_Kfolds(cutted_feature_matrix, label_matrix, 'discrim_analysis', kfolds, kfoldsAmount, plotIt);
 	fprintf('Acurácia média de classificação para discrim_analysis:\t %f\n', accuracy01);
 	%plotting the returned confusion matrix
-	if plot
+	if plotIt
 		plot_result_matrix(matrix_of_conf01, {'Maligna', 'Benigna'});
 	end
 	
 	%do the classification with the cutted_feature_matrix - I can choose the classifier at the 3º parameter
-	[accuracy02, matrix_of_conf02]= classification_Kfolds(cutted_feature_matrix, label_matrix, 'decision_tree', kfolds, kfoldsAmount, plot);
+	[accuracy02, matrix_of_conf02]= classification_Kfolds(cutted_feature_matrix, label_matrix, 'decision_tree', kfolds, kfoldsAmount, plotIt);
 	fprintf('Acurácia média de classificação para decision_tree:\t %f\n', accuracy02);
 	%plotting the returned confusion matrix
-	if plot
+	if plotIt
 		plot_result_matrix(matrix_of_conf02, {'Maligna', 'Benigna'});
 	end
 	
 	%do the classification with the cutted_feature_matrix - I can choose the classifier at the 3º parameter
[…]

### 2019-11-23 src/classification_Kfolds.m

@@ -1,4 +1,4 @@
-function [average_accuracy, total_confusion_matrix]= classification_Kfolds(feature_vectors_matrix, label_matrix, classifier, kfolds, kfoldsAmount, plot)
+function [average_accuracy, total_confusion_matrix]= classification_Kfolds(feature_vectors_matrix, label_matrix, classifier, kfolds, kfoldsAmount, plotIt)
 	%validation of the classifiers using the K-FOLDS method
 	
 	accuracy_per_fold= zeros(1, kfoldsAmount); total_confusion_matrix= zeros(2, 2); AUCroc_per_fold= zeros(1, kfoldsAmount);
@@ -30,7 +30,7 @@ function [average_accuracy, total_confusion_matrix]= classification_Kfolds(featu
 		%ROC Curve and AUC (plotting the ROC Curve for each fold and an average of the folds)
 		[Xroc, Yroc, ~, AUCroc_per_fold(i)]= perfcurve(label_matrix(idx_test, :), scores(:, 1), 'maligna');
 		
-		if plot
+		if plotIt
 			plot(Xroc, Yroc, 'LineWidth', 1.5); legends{i}= sprintf('fold %d (AUC = %.2f)', i, AUCroc_per_fold(i));
 		end
 		
@@ -48,9 +48,9 @@ function [average_accuracy, total_confusion_matrix]= classification_Kfolds(featu
 	average_AUC= mean(AUCroc_per_fold);
 	
 	%plotting the graph of ROC Curves
-	if plot
+	if plotIt
 		hold on;
-		figure; plot(intervals, mean_curve, 'Color', 'Black', 'LineWidth', 3.0);
+		figure; plotIt(intervals, mean_curve, 'Color', 'Black', 'LineWidth', 3.0);
 		legends = sprintf('Average folds AUC= %.2f', average_AUC);
 		xlabel('1 - Specificity'); ylabel('Sensitivity'); title(strcat('ROC curve: ', classifier));
 		legend(legends, 'Location', 'SE');

### 2019-11-23 src/classification_Kfolds.m
Trying to solve some bugs with graphics

@@ -30,6 +30,8 @@ function [average_accuracy, total_confusion_matrix]= classification_Kfolds(featu
 		%ROC Curve and AUC (plotting the ROC Curve for each fold and an average of the folds)
 		[Xroc, Yroc, ~, AUCroc_per_fold(i)]= perfcurve(label_matrix(idx_test, :), scores(:, 1), 'maligna');
 		
+		hold on;
+		
 		if plotIt
 			plot(Xroc, Yroc, 'LineWidth', 1.5); legends{i}= sprintf('fold %d (AUC = %.2f)', i, AUCroc_per_fold(i));
 		end
@@ -49,11 +51,11 @@ function [average_accuracy, total_confusion_matrix]= classification_Kfolds(featu
 	
 	%plotting the graph of ROC Curves
 	if plotIt
-		hold on;
-		figure; plotIt(intervals, mean_curve, 'Color', 'Black', 'LineWidth', 3.0);
+		plot(intervals, mean_curve, 'Color', 'Black', 'LineWidth', 3.0);
 		legends = sprintf('Average folds AUC= %.2f', average_AUC);
 		xlabel('1 - Specificity'); ylabel('Sensitivity'); title(strcat('ROC curve: ', classifier));
 		legend(legends, 'Location', 'SE');
-		hold off;
 	end
+	
+	hold off;
 end

### 2019-11-23 src/classification_Kfolds.m
Solved a bug on the graphics legends

@@ -58,8 +58,12 @@ function [average_accuracy, total_confusion_matrix]= classification_Kfolds(featu
 	if plotIt
 		plot(intervals, mean_curve, 'Color', 'Black', 'LineWidth', 3.0);
 		legends{i+1} = sprintf('Average folds AUC= %.2f', average_AUC);
-		xlabel('1 - Specificity'); ylabel('Sensitivity'); title(strcat('ROC curve: ', classifier));
-		legend(legends, 'Location', 'SE');
+		xlabel('1 - Specificity'); ylabel('Sensitivity');
+		title(strcat('ROC curve: ', classifier),'Interpreter', 'none');
+		try
+			legend(legends, 'Location', 'SE');
+		catch
+		end
 	end
 	
 	hold off;

### 2019-11-23 src/application.m
Just a little correction

@@ -49,8 +49,6 @@ xlabels = zeros(40,1);
 % The data for the final graphic
 results = zeros(40,4);
 
-[accuracy01, accuracy02, accuracy03, average] = classificationTests(feature_matrix, label_matrix, 6, kfoldsAmount, amountOfImages, true);
-
 % Evaluate data for each amount of descriptors from 1 up to 40
 for number_of_descriptors=1: 40
 	[accuracy01, accuracy02, accuracy03, average] = classificationTests(feature_matrix, label_matrix, number_of_descriptors, kfoldsAmount, amountOfImages, false);

### 2019-11-24 docs/article.tex
Fixed: Images and its references

@@
 According to the same study, the breast cancer is the most incident type in Brazil, with 85 620 registered cases in total, and the second most reason of mortalities among the cancers, with 18 842 cases, what represents 22\% of the total cases of breast cancer in Brazil.
-Figures 1 and 2 in the right graph the information presented until now.
+Figures \ref{fig:graphic2} and \ref{fig:graphic1} in the right graph the information presented until now.
 In the first chart is possible to visualize the statistics about the world, and in the second one is presented the numbers of cases in Brazil.
@@
     \caption{Statistics about Incidence of types of Cancer in the World \cite{GLOBOCAN}}
-    \label{fig:my_label}
+    \label{fig:graphic1}
 \end{figure}
@@
 Informations about this dataset can be found in \cite{artigo_database} and \href{https://bioimage.ucsb.edu/research/bio-segmentation}{\textbf{https://bioimage.ucsb.edu/research/bio-segmentation}}.
-The Figure 3 below presents a flowchart of the sequence of steps developed in the application.
+The Figure \ref{fig:imagem3} below presents a flowchart of the sequence of steps developed in the application.
 
@@
     \caption{Flowchart of the developed method}
-    \label{fig:my_label}
+    \label{fig:imagem3}
 \end{figure}
@@
 The segmentation was made after the filtering step, and the approach taken in the present work is to subtract the background of the segmented image from the original gray levels image.
-The code responsible for doing this task and the result produced in the image are shown in the Figure 4.
+The code responsible for doing this task and the result produced in the image are shown in the Figure \ref{fig:imagem_segmentacao}.
 
@@
 Doing this process, it is possible to reconstruct the image just with these high frequencies coefficients, that represent the edges inside the signal.
-In the Figure 8 it is possible to see the original image and the reconstructed one made from the descriptors.
+In the Figure \ref{fig:imagem_reconstrucao} it is possible to see the original image and the reconstructed one made from the descriptors.
     \item Lastly, the complex magnitude was computed for the coefficients.
-\end{itemize}{}
+\end{itemize}
 
@@
     \caption{Original Image and its reconstruction using the Fourier Descriptors}
-    \label{fig:my_label}
-\end{figure}{}
+    \label{fig:imagem_reconstrucao}
+\end{figure}
 The Local Binary Pattern Features (LBP) was described in \cite{lbp-OjalaPH96}, being a two-level version of the Texture Unit model proposed by \cite{Wang:1990:TCU:83597.83606}.
@@
 Doing this, it is possible to obtain the Fractal Dimension from each scale, as well as a General one calculated through the angular coefficient.\par
-The Figure 9 summarizes the descriptors obtained in the present work. 
+The Figure \ref{fig:table_descriptors} summarizes the descriptors obtained in the present work. 
 \begin{figure}[h]
@@
     \includegraphics[width=8.5cm]{images/table_descriptors.png}
-    \caption{Descriptors}
-    \label{fig:my_label}
-\end{figure}{}
+    \caption{Descriptors.}
+    \label{fig:table_descriptors}
+\end{figure}
 
 \section{Feature Selection}
-The feature vector composed in the last step is formed by all descriptors presented in Figure 9, but it is not a good idea providing the feature vectors with all attributes as input to the classifiers, because the probability of the classification does not achieve good results is large doing the process in this way.
+The feature vector composed in the last step is formed by all descriptors presented in Figure \ref{fig:table_descriptors}, but it is not a good idea providing the feature vectors with all attributes as input to the classifiers, because the probability of the classification does not achieve good results is large doing the process in this way.
 This can be explained from the problem so-called "Curse of Dimensionality": after a certain number of descriptors, increasing the length of the feature vector with more attributes can degrade the performance of the classifiers.\par
@@
 The performance of the proposed method was evaluated through the classifiers \textbf{Discriminant Analysis}, \textbf{Decision Tree} and \textbf{Naive Bayes}, taking into consideration that all of these classifiers were submitted to the K-Folds validation method, with K equals to 5.\par
-The best number of descriptors found by testing the classifiers used in the present method can be seen in the Figure 10, which shows the number of descriptors used for the classification in X axis, and the average rates for AUC in the Y axis.\par
-It is important to remember that the graph contained in the Figure 10 was obtained using the segmented images in the process; the best number of descriptors obtained (35) was also tested in the same process without the segmentation step, in order to determine the importance of this phase in the whole process.
-The AUC rates obtained for the Discriminant Analysis, Decision Tree and Naive Bayes were 0.83, 0.66 and 0.75 respectively, resulting in an average of 0.746, well below the value showed in the graph (0.823).
+The best number of descriptors found by testing the classifiers used in the present method can be seen in the Figure \ref{fig:finalResults}, which shows the number of descriptors used for the classification in X axis, and the average rates for AUC in the Y axis.\par
+It is important to remember that the graph contained in the Figure \ref{fig:finalResults} was obtained using the segmented images in the process; \textbf{six} was the best number of descriptors obtained, this number was also tested in the same process without the segmentation step, in order to determine the importance of this phase in the whole process.
+The AUC rates obtained for the Discriminant Analysis, Decision Tree and Naive Bayes were 0.83, 0.66 and 0.75 respectively, resulting in an average of 0.746, well below the value showed in the graph (0.82).
 This information show us that the segmentation step produces a significant improvement in the performance of the classifiers, being necessary use its during the proposed method.
 
-\begin{figure*}[h]
+\begin{figure}[h]
     \centering
-    \includegraphics[width=18.3cm]{images/chart.png}
+    \includegraphics[width=18.3cm]{images/results/finalResults.pdf}
     \caption{Average rates for AUC varying the number of descriptors taking into consideration the classifiers: Decision Tree, Discriminant Analysis and Naive Bayes}
-    \label{fig:my_label}
-\end{figure*}{}
+    \label{fig:finalResults}
+\end{figure}
 
 \section{Results}
-
-lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum,
+\par Like was shown in the previous section
 

### 2019-11-24 docs/article.tex
Almost the end! We must now review the text!

@@
 \usepackage{xcolor}
+
+\usepackage{color, colortbl}
 
@@
  T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
 \begin{document}
@@
 
+		\par The documents, code and images produced can be downloaded at \url{https://github.com/ensismoebius/Trabalho2-PDI}
+
 	\section{Image Acquisition}
 		\par The used dataset in this work is composed by 50 images of breast cells, being that 24 images are of malignant tumors and 26 of benign ones.
-Informations about this dataset can be found in \cite{artigo_database} and \href{https://bioimage.ucsb.edu/research/bio-segmentation}{\textbf{https://bioimage.ucsb.edu/research/bio-segmentation}}.
+Information about this dataset can be found in \cite{artigo_database} and \href{https://bioimage.ucsb.edu/research/bio-segmentation}{\textbf{https://bioimage.ucsb.edu/research/bio-segmentation}}.
 The Figure \ref{fig:imagem3} below presents a flowchart of the sequence of steps developed in the application.
@@
 			\end{figure}
+
 	\section{Segmentation}
@@
 		In order to obtain the more relevant descriptors and the best number of attributes, the feature vector with 7175 descriptors was examined by the ReliefF method, which is responsible for ranking the importance of the predictors based on its capability of distinguishing samples of different classes.
-The next section presents the analysis made by the ReliefF, taking into consideration the performance of the classifiers.
+The next section presents the analysis made by the Relief, taking into consideration the performance of the classifiers.
 
@@
 
+	\section{Results}
+		\par Like was shown in the previous section the number found to be the optimal in order to classify the data with the least error as possible is \textbf{six}.
+
+		\par According to the graph shown in the figure \ref{fig:finalResults} right after the amount of five descriptors its possible to note a spike witch gives the best performance in terms of classification and, after this point, the classification results slowly decay and that, at least for this problem, the \textbf{decision tree} classifier had the best results.
+
+		\par Individually, the table \ref{tab:topTenExperiment} shows the best results for each classifier, the dashed black vertical line indicates the \textit{locus} of best values.
+The confusion matrices \ref{fig:decisiontreeconfusion}, \ref{fig:discrimanalysisconfusion} and \ref{fig:naivebayesconfusion} shows the amount misclassified and correctly classified images, and finally, the ROCs curve are shown at \ref{fig:decisiontreeroc}, \ref{fig:discrimanalysisroc} and \ref{fig:naivebayesroc}.
+
+		\begin{table}[ht]
+			\centering
+			\begin{tabular}{|c|c|c|c|c|}
+				\hline 
+				Descriptors & discrim\_analysis & decision\_tree & naive\_bayes & Average \\
+				\hline 
+				1 & 0,67 & 0,59 & 0,61 & 0,63 \\
+				\hline 
+				2 & 0,76 & 0,80 & 0,76 & 0,77 \\
+				\hline 
+				3 & 0,69 & 0,76 & 0,76 & 0,74 \\
+				\hline 
+				4 & 0,69 & 0,75 & 0,78 & 0,74 \\
+				\hline 
+				5 & 0,69 & 0,74 & 0,76 & 0,73 \\
+				\hline 
+				6 & 0,77 & \textbf{0,86} & \textbf{0,83} & \textbf{0,82} \\
+				\hline 
+				7 & 0,79 & 0,82 & \textbf{0,83} & 0,82 \\
+				\hline 
+				8 & \textbf{0,81} & 0,78 & 0,81 & 0,80 \\
+				\hline 
+				9 & \textbf{0,81} & 0,78 & 0,77 & 0,79 \\
+				\hline 
+				10 & 0,77 & 0,82 & 0,79 & 0,80\\
+				\hline 
+			\end{tabular} 
+			\caption{First ten results of experiment (The best values highlighted)}
+			\label{tab:topTenExperiment}
+		\end{table}
 		\begin{figure}[h]
 			\centering
-    \includegraphics[width=18.3cm]{images/results/finalResults.pdf}
+			\includegraphics[width=0.5\textwidth]{images/results/finalResults.pdf}
 			\caption{Average rates for AUC varying the number of descriptors taking into consideration the classifiers: Decision Tree, Discriminant Analysis and Naive Bayes}
@@
 		\end{figure}
+		\begin{figure}[hb]
+			\centering
+			\includegraphics[width=0.7\linewidth]{images/results/decision_treeConfusion}
+			\caption{Decision tree confusion matrix}
+			\label{fig:decisiontreeconfusion}
+		\end{figure}
 
-\section{Results}
-\par Like was shown in the previous section
+		\begin{figure}[ht]
+			\centering
+			\includegraphics[width=0.7\linewidth]{images/results/discrim_analysisConfusion}
+			\caption{Discriminate analysis confusion matrix}
+			\label{fig:discrimanalysisconfusion}
+		\end{figure}
+
+		\begin{figure}[ht]
+			\centering
+			\includegraphics[width=0.7\linewidth]{images/results/naive_bayesConfusion}
+			\caption{Naive Bayes confusion matrix}
+			\label{fig:naivebayesconfusion}
+		\end{figure}
+
+		\begin{figure}[!htp]
+			\centering
+			\includegraphics[width=0.7\linewidth]{images/results/decision_treeROC}
+			\caption{Decision tree ROC curve}
+			\label{fig:decisiontreeroc}
+		\end{figure}
+
+		\begin{figure}[!htp]
+			\centering
+			\includegraphics[width=0.7\linewidth]{images/results/discrim_analysisROC}
+			\caption{Discriminate analysis ROC curve}
+			\label{fig:discrimanalysisroc}
+		\end{figure}
+
+		\begin{figure}[!htp]
+			\centering
+			\includegraphics[width=0.7\linewidth]{images/results/naive_bayesROC}
+			\caption{Naive Bayes ROC curve}
+			\label{fig:naivebayesroc}
+		\end{figure}
 
 	\section{Conclusion}
-lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum, lorem ipsum,
+		\par The classification without the filtering and segmentation steps are noticeably worse, so these phases of the image processing are crucial for a good classification performance.
+		\par It is important to note that find the right number of descriptors for each method of classification raises the accuracy of algorithms although it can be a heavy work for the computer.
 

### 2019-11-24 docs/article.tex
Orthographic and style review are ready!

@@
 	\begin{abstract}
-		According to the recent survey published by the International Agency for Research on Cancer (IARC), the breast cancer is one of the most common kinds of cancers diagnosed in the population nowadays.
+		According to the recent survey published by the International Agency for Research on Cancer (IARC), breast cancer is one of the most common kinds of cancers diagnosed in the population nowadays.
 The diagnosis of this type of disease is usually made through the analysis of the breast cells by a specialist after the biopsy and staining, normally made by the combination of hematoxylin and eosin (H \& E).
 This manual assessment is a time-consuming task and depends on the expertise and perception of the pathologists.
-In order to overcome this limitations, image processing can be considered as great aid alternative.
+In order to overcome these limitations, image processing can be considered a great aid alternative.
 In this paper is presented an application for the classification of breast cell images between malignant and benign tumors.
-The developed software includes the principals steps present within the image processing field, such as preprocessing, segmentation, feature extraction and classification, in order to achieve good results in the analysis of a dataset composed by 50 images of malignant and benign tumors.
+The developed software includes the main steps present within the image processing field, such as preprocessing, segmentation, feature extraction and classification, in order to achieve good results in the analysis of a dataset composed of 50 images of malignant and benign tumors.
 	\end{abstract}
@@
 In a recent survey called GLOBOCAN \cite{GLOBOCAN} published in 2018 by the IARC, can be visualized the statistics about this type of cancer around the world.
-The study states that the breast cancer is the second most incident type of cancer in world, with 2 088 049 cases of this disease in the last year, and the number of cases of mortality is equals to 626 679 (about 30\% of total).
+The study states that breast cancer is the second most incident type of cancer in the world, with 2 088 049 cases of this disease in the last year, and the number of cases of mortality is equaled to 626 679 (about 30\% of total).
 According to the same study, the breast cancer is the most incident type in Brazil, with 85 620 registered cases in total, and the second most reason of mortalities among the cancers, with 18 842 cases, what represents 22\% of the total cases of breast cancer in Brazil.
@@
 
-		\par The process of the diagnosis of this type of cancer is usually made by a specialist called pathologist, who is responsible for analysing breast cells acquired through two steps: biopsy and staining.
-The biopsy step is a test that removes tissues or fluids from the suspicious breast area, and this procedure is the only one that can definitely define if the suspected area is cancerous or not.
-The staining step is responsible for add color to the cells in order to become easier the visualization of the tissue by the pathologist.
-After this two steps, the specialized doctor analyses the tissue through a microscope in order to determine if the there are malignant tumors or benign ones.
-As can be seen, the diagnosis is a really time-consuming task, which depends strongly of the expertise of the specialist.
-Therefore, is interesting the possibility of having applications that analyse digital images of this breast cells and be able to assist the doctor in the process of diagnosis.
+		\par The process of the diagnosis of this type of cancer is usually made by a specialist called pathologist, who is responsible for analyzing breast cells acquired through two steps: biopsy and staining.
+The biopsy step is a test that removes tissues or fluids from the suspicious breast area, and this procedure is the only one that can define if the suspected area is cancerous or not.
+The staining step is responsible for add color to the cells to become easier the visualization of the tissue by the pathologist.
+After these two steps, the specialized doctor analyses the tissue through a microscope to determine if there are malignant tumors or benign ones.
+As can be seen, the diagnosis is a time-consuming task, which depends strongly on the expertise of the specialist.
+Therefore, is interesting the possibility of having applications that analyze digital images of these breast cells and be able to assist the doctor in the process of diagnosis.
 
-		\par The Digital Image Processing is the computational field responsible for dealing with this kind of task, which involves some steps for processing the image in order to achieve the better possible classification rate, in this case between malignant and benign tumors.
-This paper presents the steps present within of the development of an application responsible for classifying images of breast cells from features extracted, which will be described in the sequence of the paper.
-Some measures as accuracy, ROC Curve and AUC are compared in order to indicate the best combination of features and classifier.
-The rest of the paper is organized as follow:  Section II is responsible for presenting the image acquisition, while the section III demonstrates how the filtering of the images was made.
-Section IV presents the segmentation step, and its impact in the following phases.
+		\par The Digital Image Processing is the computational field responsible for dealing with this kind of task, which involves some steps for processing the image to achieve a better possible classification rate, in this case between malignant and benign tumors.
+This paper presents the steps present within the development of an application responsible for classifying images of breast cells from features extracted, which will be described in the sequence of the paper.
+Some measures as accuracy, ROC Curve and AUC are compared to indicate the best combination of features on classifiers.
+The rest of the paper is organized as follows:  Section II is responsible for presenting the image acquisition, while section III demonstrates how the filtering of the images was made.
+Section IV presents the segmentation step and its impact in the following phases.
 The step of feature extraction is presented in Section V and the feature selection in Section VI.
-Finishing the paper, the Section VII presents the process of classification, while Sections VIII and IX present the results and conclusion respectively.
+Finishing the paper, Section VII presents the process of classification, while Sections VIII and IX present the results and conclusion respectively.
 
@@
 	\section{Image Acquisition}
-		\par The used dataset in this work is composed by 50 images of breast cells, being that 24 images are of malignant tumors and 26 of benign ones.
+		\par The used dataset in this work is composed of 50 images of breast cells, being that 24 images are of malignant tumors and 26 of benign ones.
 Information about this dataset can be found in \cite{artigo_database} and \href{https://bioimage.ucsb.edu/research/bio-segmentation}{\textbf{https://bioimage.ucsb.edu/research/bio-segmentation}}.
@@
 		\subsection{Filtering and masking}
-			Two kinds of filters were used:
-			\par A low pass filter, witch is used to highlight the low frequencies features of the image, with radius of  empirically determined 50 pixels, and a high pass filter, to enhance the detailed information at the image, with  radius of one.
+            \par Two kinds of filters were used:
+			\par A low pass filter, which is used to highlight the low frequencies features of the image, with a radius of empirically determined 50 pixels, and a high pass filter, to enhance the detailed information at the image, with a radius of one.
 
@@
 	\section{Segmentation}
-		\par The segmentation is an important step within the image processing, which is responsible for subdividing  an image in regions or objects that compose the signal \cite{Gonzalez:2006:DIP:1076432}, usually, this process is made through the separation of the image between background and object.
+        \par The segmentation is an important step within the image processing, which is responsible for subdividing an image into regions or objects that compose the signal \cite{Gonzalez:2006:DIP:1076432}, usually, this process is made through the separation of the image between background and object.
 Several techniques can be used in this process, such as based on thresholding, edge detection, region approaches.
@@
 The segmentation was made after the filtering step, and the approach taken in the present work is to subtract the background of the segmented image from the original gray levels image.
-The code responsible for doing this task and the result produced in the image are shown in the Figure \ref{fig:imagem_segmentacao}.
+The code responsible for doing this task and the result produced in the image are shown in Figure \ref{fig:imagem_segmentacao}.
 
@@
 
-		\par Although visually is difficult to realize differences between the original image and the segmented one, was checked during the tests that for this image 223 682 pixels were modified in the resulted image in comparison with the original one.
-Since the dataset is composed for images of resolution 896x768, this quantity of modified pixels achieve around 32\% of the total.
-
-		\par Before proceeding for a description of the next steps, it is important to say that the segmentation step is not always necessary in image processing; usually, this step is applied when the following steps as feature extraction and classification are not presenting good results and it is needed to improve the process.\par
-		Taking this in consideration, in the next sections is presented some measures of classification for segmented and non segmented images, in order to determine the importance and necessity of this step in the whole process.
+		\par Although visually is difficult to realize differences between the original image and the segmented one was checked during the tests that for this image 223 682 pixels were modified in the resulted image in comparison with the original one.
+Since the dataset is composed of images of resolution 896x768, this quantity of modified pixels achieves around 32\% of the total.
+		\par Before proceeding for a description of the next steps, it is important to say that the segmentation step is not always necessary in image processing; usually, this step is applied when the following steps as feature extraction and classification are not presenting good results and it is needed to improve the process.
+		\par Taking this into consideration, the next sections have presented some measures of classification for segmented and non-segmented images, to determine the importance and necessity of this step in the whole process.
 
 	\section{Feature Extraction}
-		The Feature Extraction can be considered as one of the most important steps in Image Processing: this is the last phase before the classification of the samples.
-So, the main objective here is to compose feature vectors capable to describe the samples, in order to classify correctly each example in its real class.\par
-		Commonly, two approaches can be chosen in order to extract descriptors from an image: Handcrafted Features and Non-Handcrafted ones.
-The Handcrafted Features, as the name claims, are the descriptors extracted manually, according to choice of the developer, while the Non-Handcrafted Features are extracted in an automatic way, in order to do the best possible classification (one example of this approach are the Convolutional Neural Networks - CNN).
-\par
-		As mentioned in the title of this paper, the used approach for extracting the descriptors from the histopathological images was the handcrafted one, where 11 descriptors were extracted and used as the input of the classifiers.
+        \par The Feature Extraction can be considered as one of the most important steps in Image Processing: this is the last phase before the classification of the samples.
+So, the main objective here is to compose feature vectors capable to describe the samples, to classify correctly each example in its real class.
+        \par Commonly, two approaches can be chosen to extract descriptors from an image: Handcrafted Features and Non-Handcrafted ones.
+The Handcrafted Features, as the name claims, are the descriptors extracted manually, according to the choice of the developer, while the Non-Handcrafted Features are extracted automatically, to do the best possible classification (one example of this approach are the Convolutional Neural Networks - CNN).
+		\par As mentioned in the title of this paper, the used approach for extracting the descriptors from the histopathological images was the handcrafted one, where 11 descriptors were extracted and used as the input of the classifiers.
 It is important to remember that the extraction was accomplished from segmented images and non-segmented ones, so, it is possible to compare the impact of the segmentation step during the classification.
-Below is presented the extracted features used in the process.\par
-		The descriptors used in the present process can be divided into 3 categories: First Order Measures, Second Order Measures and Others.
-The First Order Measures are the descriptors that consider just the gray level information about the pixels, not considering the spatial relation among them.
-The Second Order Measures, instead of the first ones, consider the spatial relation among the pixels, beyond the gray level property.
+Below are the extracted features used in the process.
+		\par The descriptors used in the present process can be divided into 3 categories: First Order Measures, Second Order Measures and Others.
+The First Order Measures are the descriptors that consider just the gray level information about the pixels, not considering the spatial relationships among them.
+The Second Order Measures, instead of the first ones, consider the spatial relationships among the pixels, beyond the gray level property.
 These descriptors are extracted from the called Gray Level Co-occurrence Matrix (GLCM), that is responsible to store the frequency that a pixel with gray level \textbf{i} and other with gray level \textbf{j} occur in the image, separated for a distance \textbf{d}, in the direction\textbf{ $\theta$} \cite{conci2008computacao}.
-This method was proposed in 1973 by \cite{haralick:smc1973}, and the descriptors extracted from the GLCM are called Haralick descriptors (in the present work 6 of the 14 descriptors proposed by Haralick were used).\par
-		The ther group mentioned in the paragraph above includes the descriptors that do not fit the First and Second Measures, so, becomes important to explain how these descriptors were extracted in the proposed method.
+This method was proposed in 1973 by \cite{haralick:smc1973}, and the descriptors extracted from the GLCM are called Haralick descriptors (in the present work 6 of the 14 descriptors proposed by Haralick were used).
+		\par The group mentioned in the paragraph above includes the descriptors that do not fit the First and Second Measures, so, becomes important to explain how these descriptors were extracted in the proposed method.
 Three descriptors can be found in this last group: Fourier Descriptors, Local Binary Pattern Features and Fractal Dimension Descriptors.
-\par
-		The Fourier Descriptors (FD), as the name say, are the features extracted from the Fourier Transform, that is responsible to transform the visualization of the signal from the spatial domain to the frequency domain, in order to become possible to see the frequencies that compose the image.
+		\par The Fourier Descriptors (FD), as the name says, are the features extracted from the Fourier Transform, which is responsible to transform the visualization of the signal from the spatial domain to the frequency domain, to become possible to see the frequencies that compose the image.
 Different approaches can be chosen to extract the FD`s, in the present work the proposed process was as follows:
@@
             \item The image was transformed to the frequency domain with the Fast Fourier Transform (FFT).
-		    \item Without doing the shift of the transformed, a number of N coefficients in the middle of the spectrum were taken, so just the high frequencies was caught from the FFT.
+			\item Without doing the shift of the transformed, N coefficients in the middle of the spectrum was taken, so just the high frequencies were caught from the FFT.
 Doing this process, it is possible to reconstruct the image just with these high frequencies coefficients, that represent the edges inside the signal.
-In the Figure \ref{fig:imagem_reconstrucao} it is possible to see the original image and the reconstructed one made from the descriptors.
+In Figure \ref{fig:imagem_reconstrucao} it is possible to see the original image and the reconstructed one made from the descriptors.
 			\item Lastly, the complex magnitude was computed for the coefficients.
@@
 		\end{figure}
-		The Local Binary Pattern Features (LBP) was described in \cite{lbp-OjalaPH96}, being a two-level version of the Texture Unit model proposed by \cite{Wang:1990:TCU:83597.83606}.
-The main idea is describe the image considering a neighborhood of 3x3 pixels and comparing the gray levels.\par
-		The Fractal Dimension Descriptors extracted in the present work were obtained using the Box Counting Theorem, a method where the image is divided into N windows according to a certain scale and the number of boxes that contains the objects that must be counted.
-Doing this, it is possible to obtain the Fractal Dimension from each scale, as well as a General one calculated through the angular coefficient.\par
-		The Figure \ref{fig:table_descriptors} summarizes the descriptors obtained in the present work. 
+        \par The Local Binary Pattern Features (LBP) was described in \cite{lbp-OjalaPH96}, being a two-level version of the Texture Unit model proposed by \cite{Wang:1990:TCU:83597.83606}.
+The main idea is to describe the image considering a neighborhood of 3x3 pixels and comparing the gray levels.
+		\par The Fractal Dimension Descriptors extracted in the present work were obtained using the Box Counting Theorem, a method where the image is divided into N windows according to a certain scale and the number of boxes that contains the objects that must be counted.
+Doing this, it is possible to obtain the Fractal Dimension from each scale, as well as a General one calculated through the angular coefficient.
+		\par Figure \ref{fig:table_descriptors} summarizes the descriptors obtained in the present work. 
 		\begin{figure}[h]
@@
 	\section{Feature Selection}
-		The feature vector composed in the last step is formed by all descriptors presented in Figure \ref{fig:table_descriptors}, but it is not a good idea providing the feature vectors with all attributes as input to the classifiers, because the probability of the classification does not achieve good results is large doing the process in this way.
-This can be explained from the problem so-called "Curse of Dimensionality": after a certain number of descriptors, increasing the length of the feature vector with more attributes can degrade the performance of the classifiers.\par
-		In order to obtain the more relevant descriptors and the best number of attributes, the feature vector with 7175 descriptors was examined by the ReliefF method, which is responsible for ranking the importance of the predictors based on its capability of distinguishing samples of different classes.
+        \par The feature vector composed in the last step is formed by all descriptors presented in Figure \ref{fig:table_descriptors}, but it is not a good idea.
+Providing the feature vectors with all attributes as input to the classifiers gives a high probability of the classification does not achieve good results.
+This can be explained from the so-called "Curse of Dimensionality": After a certain number of descriptors, increasing the length of the feature vector with more attributes can degrade the performance of the classifiers.
+		\par In order to obtain the more relevant descriptors and the best number of attributes, the feature vector with 7175 descriptors was examined by the ReliefF method, which is responsible for ranking the importance of the predictors based on its capability of distinguishing samples of different classes.
 The next section presents the analysis made by the Relief, taking into consideration the performance of the classifiers.
@@
 	\section{Classification}
-		The relevance of the descriptors, as well the performance of the classifiers were measured by the analysis of ROC Curve and area under curve ROC (AUC).
-This measures were used in the proposed method because the malignant an benign classes are unbalanced in dataset, considering that there are 24 malignant samples and 26 benign ones.
-Taking this is consideration, it is not a good idea analysing the obtained results through measures as accuracy, because the calculation of this last measure does not take the class balancing into consideration.\par
-		The ROC Curve and AUC allow to analyse the performance of the classifiers through the confusion matrix obtained varying the threshold, so the plotted graph is formed by the X axis (1 - Specificity) and Y (Sensitivity), therefore, the AUC with value equals to 1 represents a perfect classification, while an AUC equals to 0.5 or less represents a random classification.\par
-		The performance of the proposed method was evaluated through the classifiers \textbf{Discriminant Analysis}, \textbf{Decision Tree} and \textbf{Naive Bayes}, taking into consideration that all of these classifiers were submitted to the K-Folds validation method, with K equals to 5.\par
-		The best number of descriptors found by testing the classifiers used in the present method can be seen in the Figure \ref{fig:finalResults}, which shows the number of descriptors used for the classification in X axis, and the average rates for AUC in the Y axis.\par
-		It is important to remember that the graph contained in the Figure \ref{fig:finalResults} was obtained using the segmented images in the process; \textbf{six} was the best number of descriptors obtained, this number was also tested in the same process without the segmentation step, in order to determine the importance of this phase in the whole process.
-The AUC rates obtained for the Discriminant Analysis, Decision Tree and Naive Bayes were 0.83, 0.66 and 0.75 respectively, resulting in an average of 0.746, well below the value showed in the graph (0.82).
-This information show us that the segmentation step produces a significant improvement in the performance of the classifiers, being necessary use its during the proposed method.
+        \par The relevance of the descriptors, as well as the performance of the classifiers were measured by the analysis of ROC Curve and area under curve ROC (AUC).
+These measures were used in the proposed method because the malignant and benign classes are unbalanced in the dataset, considering that there are 24 malignant samples and 26 benign ones.
+Taking this into consideration, it is not a good idea analyzing the obtained results through measures as accuracy, because the calculation of this last measure does not take the class balancing into consideration.
+		\par The ROC Curve and AUC allow to analyze the performance of the classifiers through the confusion matrix obtained varying the threshold, so the plotted graph is formed by the X axis (1 - Specificity) and Y (Sensitivity), therefore, the AUC with value equals to 1 represents a perfect classification, while an AUC equals to 0.5 or less represents a random classification.
+		\par The performance of the proposed method was evaluated through the classifiers \textbf{Discriminant Analysis}, \textbf{Decision Tree} and \textbf{Naive Bayes}, taking into consideration that all of these classifiers were submitted to the K-Folds validation method, with K equals to 5.
+		\par The best number of descriptors found by testing the classifiers used in the present method can be seen in the Figure \ref{fig:finalResults}, which shows the number of descriptors used for the classification in the X axis, and the average rates for AUC in the Y axis.
+		\par It is important to remember that the graph contained in the Figure \ref{fig:finalResults} was obtained using the segmented images in the process; \textbf{six} was the best number of descriptors obtained, this number was also tested in the same process without the segmentation step, in order to determine the importance of this phase in the whole process.
+The AUC rates obtained for the Discriminant Analysis, Decision Tree and Naive Bayes were 0.83, 0.66 and 0.75 respectively, resulting in an average of 0.746, well below the value shown in the graph (0.82).
+This information shows us that the segmentation step produces a significant improvement in the performance of the classifiers, being necessary to use it during the proposed method.
 
 	\section{Results}
-		\par Like was shown in the previous section the number found to be the optimal in order to classify the data with the least error as possible is \textbf{six}.
+        \par Like was shown in the previous section the number found to be optimal to classify the data with the least error as possible is \textbf{six}.
 
@@
 			\end{tabular} 
-			\caption{First ten results of experiment (The best values highlighted)}
+			\caption{First ten results of experiment, best values highlighted}
 			\label{tab:topTenExperiment}
@@
 	\section{Conclusion}
-		\par The classification without the filtering and segmentation steps are noticeably worse, so these phases of the image processing are crucial for a good classification performance.
+		\par The classification without the filtering and segmentation steps are noticeably worse, so these phases of the image processing are crucial for good classification performance.
 		\par It is important to note that find the right number of descriptors for each method of classification raises the accuracy of algorithms although it can be a heavy work for the computer.

### 2019-11-25 docs/article.tex
últimos ajustes - pastas com imagens foram colocadas no caminho já

@@
 In a recent survey called GLOBOCAN \cite{GLOBOCAN} published in 2018 by the IARC, can be visualized the statistics about this type of cancer around the world.
-The study states that breast cancer is the second most incident type of cancer in the world, with 2 088 049 cases of this disease in the last year, and the number of cases of mortality is equaled to 626 679 (about 30\% of total).
+The study states that breast cancer is the second most incident type of cancer in the world, with 2 088 049 cases of this disease in the last year, and the number of cases of mortality is equals to 626 679 (about 30\% of total).
 According to the same study, the breast cancer is the most incident type in Brazil, with 85 620 registered cases in total, and the second most reason of mortalities among the cancers, with 18 842 cases, what represents 22\% of the total cases of breast cancer in Brazil.
-Figures \ref{fig:graphic2} and \ref{fig:graphic1} in the right graph the information presented until now.
+Figures \ref{fig:graphic1} and \ref{fig:graphic2} in the right graph the information presented until now.
 In the first chart is possible to visualize the statistics about the world, and in the second one is presented the numbers of cases in Brazil.
@@
 This method was proposed in 1973 by \cite{haralick:smc1973}, and the descriptors extracted from the GLCM are called Haralick descriptors (in the present work 6 of the 14 descriptors proposed by Haralick were used).
-		\par The group mentioned in the paragraph above includes the descriptors that do not fit the First and Second Measures, so, becomes important to explain how these descriptors were extracted in the proposed method.
+		\par The "others group" mentioned in the paragraph above includes the descriptors that do not fit the First and Second Measures, so, becomes important to explain how these descriptors were extracted in the proposed method.
 Three descriptors can be found in this last group: Fourier Descriptors, Local Binary Pattern Features and Fractal Dimension Descriptors.
@@
 	\section{Feature Selection}
-        \par The feature vector composed in the last step is formed by all descriptors presented in Figure \ref{fig:table_descriptors}, but it is not a good idea.
+        \par The feature vector composed in the last step is formed by all descriptors presented in Figure \ref{fig:table_descriptors}, but it is not a good idea to make a classification with all these descriptors.
 Providing the feature vectors with all attributes as input to the classifiers gives a high probability of the classification does not achieve good results.

### 2019-11-25 src/application.m

@@ -2,8 +2,8 @@
 kfoldsAmount=5;
 
 %calling the function for reading the folder of images
-maligna_images= image_reader('.\samples\Roi_Recort_bisque_Maligna');
-benigna_images= image_reader('.\samples\Roi_Recort_bisque_Benigna');
+maligna_images= image_reader('Roi_Recort_bisque_Maligna');
+benigna_images= image_reader('Roi_Recort_bisque_Benigna');
 
 %filtering the images (choose % of the total) -- 1 == all images
 maligna_images= filtering_images(maligna_images, 1);
